### 2017-02-25 IARC_Paper/Paper.tex
Add paper and mission rules

\documentclass{article}

\usepackage{geometry}
\geometry{letterpaper}
\usepackage{doc}
\usepackage{url}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{fancyhdr}

\title{IARC Research Paper}
\author{Texas Aerial Robotics}
\date{February 25, 2017}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\cfoot{\thepage\ of \pageref{LastPage}}

\begin{document}
\maketitle
\thispagestyle{empty}

\abstract{
Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017. The goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter. We use an Intel stereo camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter. 
}

\pagebreak
\tableofcontents

\pagebreak

\section{Introduction}
\label{introduction}

Description of mission with link to rules.

\section{Background, Preliminary, and Related Work}

Describe history, work, or projects that serve as direct contributors to the subject of your research paper

\section{Quadcopter}

Vehicle information

\subsection{Hardware}

Probably have a table for what is what.

\subsection{Controls}

\subsection{Vision}

\subsection{Business}

\section{Safety}

\section{Simulations}

\section{Conclusion}

Hopefully we do well at Georgia Tech! gl hf!

\section{Acknowledgements}

\bibliography{Paper}
\bibliographystyle{unsrt}

\end{document}

### 2017-05-28 IARC_Paper/Paper.tex
Time to get working on this

@@
 
-\usepackage{geometry}
+\usepackage[margin=1in]{geometry}
 \geometry{letterpaper}
@@
 \title{IARC Research Paper}
-\author{Texas Aerial Robotics}
-\date{February 25, 2017}
+\author{Texas Aerial Robotics \\ \\ Samid Ahmed, Adam Bays, Nicholas Boeker, Jeremie Gallegos, \\ Eric Johnson, Aaron Karns, Cameron Lane, Juliette Licon, \\ Mark Loveland, Jonathan Lu, Umer Salman, Ethan Starr, Jacob Yanez} % A note about authors:  list only those who actually contributed to the writing of this paper.
+All the members of the team should not be listed as authors unless they all wrote at least a page of the material for the paper.
+
+\date{May 28, 2017}
 
@@
 \fancyhead{}
-\cfoot{\thepage\ of \pageref{LastPage}}
+\cfoot{\textsf{Page \thepage\ of \pageref{LastPage}}}
 
@@
 The goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter.
-We use an Intel stereo camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
+We use a camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
 }
@@
 \section{Safety}
+\subsection{Pre-flight Checklist}
+\begin{enumerate}
+	\item Make sure lidar and pix flow are not covered
+	\item Make sure that escs are plugged in to the right ports. 
+	\item Make sure that the props are on in the correct direction. 
+	\item Make sure that the props are not upside down
+	\item Make sure drone is level before powering on
+	\item Hold safety button
+	\item Make sure ground station has good telemetry
+	\item Verify critical sensors are giving good data
+	\item Make sure everyone is clear of drone 
+\end{enumerate}
 

### 2017-05-29 IARC_Paper/Paper.tex
Wrote a decent bit of the paper. Still needs some pics, diagrams, specifications, etc.

--- 2017-02-25 IARC_Paper/Paper.tex
@@
-\documentclass{article}
-
-\usepackage{geometry}
+\documentclass[12pt]{article}
+\usepackage[margin=1in]{geometry}
 \geometry{letterpaper}
@@
 \usepackage{graphicx}
+\usepackage{gensymb}
 \usepackage{fancyhdr}
+\usepackage{hyperref}
 
-\title{IARC Research Paper}
-\author{Texas Aerial Robotics}
-\date{February 25, 2017}
+\title{IARC Technical Paper}
+\author{
+	\textbf{Texas Aerial Robotics} \\ 
+	\textit{University of Texas at Austin} \\ \\ 
+%	Austin, TX 78705 \\ 
+	\href{mailto:TexasAerialRobotics@gmail.com}{TexasAerialRobotics@gmail.com} \\ \\ 
+	Samid Ahmed, Adam Bays, Nicholas Boeker, Jeremie Gallegos, \\ Eric Johnson, Aaron Karns, Cameron Lane, Juliette Licon, \\ Mark Loveland, Jonathan Lu, Umer Salman, Ethan Starr, Jacob Yanez \\ \\ Dr.
+Akela, Marcelino}
+% A note about authors:  list only those who actually contributed to the writing of this paper.
+All the members of the team should not be listed as authors unless they all wrote at least a page of the material for the paper.
+
+\date{May 28, 2017}
 
@@
 Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017.
-The goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter.
-We use an Intel stereo camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
+Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
+The mission takes place in a GPS denied environment, so gridlines will be used as reference positions.
 }
 
-\pagebreak
-\tableofcontents
+% \pagebreak
+% \tableofcontents
 
@@
 \section{Introduction}
-\label{introduction}
+\subsection{The Mission}
+Mission 7a of IARC consists of developing an aerial vehicle that can interact with moving ground robots.
+Those ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions.
+The vehicle must herd the 10 Roombas across one side of the 20 meter by 20 meter grid.
+Additionally, 4 obstacle Roombas have PVC poles the vehicle must avoid.
+The way the vehicle must herd the Roombas is by either blocking the forward motion of the Roomba, directing it to rotate 180\degree, or tapping the pressure plate atop the Roomba, directing the Roomba to rotate 45\degree clockwise.
 
-Description of mission with link to rules.
+An added difficulty to the mission is that the setting is a (Global Positioning System) GPS denied environment.
+Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid.
+Thus, we determined that we needed to design other methods to determine our positioning.
+By using a camera to observe the gridlines and an Inertial Measurement Unit (IMU), we are working our way to determining where the vehicle is on the grid.
 
-\section{Background, Preliminary, and Related Work}
+Mission 7b will add in an additional aerial vehicle to compete against for herding more Roombas.
 
-Describe history, work, or projects that serve as direct contributors to the subject of your research paper
+\subsection{Yearly milestones}
+This is the first time Texas Aerial Robotics is competing in any event. Our goal for the year was to be competitive at this year's IARC.
 
 \section{Quadcopter}
-
-Vehicle information
+We decided to fabricate a quadcopter with aluminum arms with a carbon fiber base.
+During build, we laser-cut wood for the base to allow for rapid iterating.
+Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions.
+Our quadrotor needed to house all of the sensors for operation with sufficient flight time.
 
 \subsection{Hardware} 
-
-Probably have a table for what is what.
+At the end of the aluminum arms sit four (insert here) motors for lift.
+The four motors provide (insert) grams of lift, a sufficient amount for our (insert) gram quadcopter.
+The arms are fixed into the base pieces, which do not pass enough vibration to the sensors that we needed any additional vibration damping.
 
 \subsection{Controls}
+We use a Pixhawk flight controller, situated directly center of the quadcopter, for flying and sensor capabilities.
+We supplement the Pixhawk's accelerometer, gyroscope, and compass with an optical flow sensor (PX4FLOW) for position tracking and a LIDAR (LIDAR Lite v3) for altitude measurements.
+These sensors allow the Pixhawk to better maneuver and stabilize the flight of the vehicle.
 
@@
 \section{Safety}
+\subsection{Pre-flight Checklist}
+\begin{enumerate}
+	\item Check LIDAR and flow sensor are not covered 
+	\item Check ESCs are plugged into correct ports 
+	\item Check props are on in the correct direction 
+	\item Check props are not upside down
+	\item Check that drone is level before powering on
+	\item Hold safety button
+	\item Make sure ground station has good telemetry
+	\item Verify critical sensors are giving good data
+	\item Make sure everyone is clear of drone 
+\end{enumerate}
+\subsection{Kill Switch}
+Kill Switch
+
+\subsection{Prop Guards}
+Our prop guards took multiple iterations.
+We wanted a design that would not interfere with the prop wash, but still be able to avoid the quadcopter from destroying itself in the unfortunate event it collides with something.
+The first iteration looked nice, but interfered with the prop wash too much and weighted too much, reducing the thrust.
 
 \section{Simulations}
+Another aspect of our research into solving Mission 7 involved simulating the arena and quadcopter on the computer to allow us to test without fear of damaging the quadcopter.
+It also allowed us to test with a full field and simulated Roombas as we currently do not have a physical field setup or more than one Roomba.
+
+To simulate the quadcopter, we use Ardupilot's Software in the Loop (SITL) simulation method to run a Gazebo simulation with ROS.
+Using the PX4 flight stack, we are able to simulate a quadcopter like ours with a Pixhawk and Optical Flow sensor.
+
+To simulate the Roombas, we use a SDF model found online which we duplicated to get the 10 objective Roombas and 4 obstacle Roombas.
+We can simulate the randomized motion by issuing ROS commands to the Roombas.
 
 \section{Conclusion}
+We still have quite a ways to go before we can consider ourselves competitive.
+Due to the fact that we started our organization in 2017, we have come a long way and learned a lot, yet we plan to continue work to beat this mission as quick as possible.
+Hopefully we do well at Georgia Tech!
 
-Hopefully we do well at Georgia Tech! gl hf!
+\section{Acknowledgments}
+We are thankful for Dr. Akela at UT Austin. Additionally, we are thankful for UT Austin's Aerospace Department for providing us with a meeting room and sponsorship.
 
-\section{Acknowledgements}
-
+We also would not have been able to work towards this mission without the sponsorship of General Dynamics. 
 \bibliography{Paper}

### 2017-05-31 IARC_Paper/Paper.tex
Added more info and some refrences!!11!

@@
 \usepackage{fancyhdr}
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
 \usepackage{hyperref}
@@
 	\href{mailto:TexasAerialRobotics@gmail.com}{TexasAerialRobotics@gmail.com} \\ \\ 
-	Samid Ahmed, Adam Bays, Nicholas Boeker, Jeremie Gallegos, \\ Eric Johnson, Aaron Karns, Cameron Lane, Juliette Licon, \\ Mark Loveland, Jonathan Lu, Umer Salman, Ethan Starr, Jacob Yanez \\ \\ Dr.
-Akela, Marcelino}
-% A note about authors:  list only those who actually contributed to the writing of this paper.
-All the members of the team should not be listed as authors unless they all wrote at least a page of the material for the paper.
+	Samid Ahmed, Nicholas Boeker, Eric Johnson, \\ Aaron Karns, Mark Loveland, Umer Salman}
 
@@
 
-% \pagebreak
-% \tableofcontents
+\pagebreak
+\tableofcontents
 
@@
 
+\subsection{Faculty Support}
+At the beginning of the creation of Texas Aerial Robotics, the team searched for professors to provide technical guidance for the project.
+Within the UT Department of Aerospace TAR reached out to Dr.
+Maruthi Akella.
+Dr.
+Akella has been conducting research in areas similar to the core objectives of IARC’s Mission 7.
+Dr.
+Akella has been doring research to create agile intelligent quadrotors in environments free of GPS.
+Dr.
+Akella expressed interest in Mission 7 as soon the team reached out.
+From the outset of the relationship Dr.
+Akella has provided expertise, access to his grad students as well as access to his indoor and outdoor lab.
+Dr.
+Akella also introduced us to multiple corporation looking to sponsor student projects.
+TAR is incredibly thankful to have the support of Dr.
+Akella.
+
+\subsection{Team Structure}
+As important as the drone a team develops, is the process in which it is developed.
+The past year has been Texas Aerial Robotics(TAR) maiden year and the team has put a lot of effort in developing the process to catalyze the engineering of the drone.
+During the fall semester, the team made just about every mistake in the book with regards to how to run a competition team.
+The team struggled with communication, vision and drive.
+This disorganization resulted with TAR ending the first semester with little to no progress.
+With the failure of the semester came the resignation of our president.
+Texas Aerial Robotics was at a crossroads.
+
+The winter break was used as a period of reflection.
+At the start of the new semester a new president was elected and a formal management style was implemented.
+Scrum.
+This is short term, agile style of management that makes short term goals and reflects and resets for the next “scrum”.
+Along with scrum, the team implemented organizational apps such as slack and trello.
+Slack allowed the team to keep all the sub-team conversations separate, but unified.
+This kept members from silencing their line of communication as well as still allowing members to view what the other sub-teams are working on.
+Automated reminders for meetings were also set up through slack to prevent members from forgetting their duties to the team.
+Trello was an incredible addition to our organizational platform.
+Trello is a ubiquitous bulletin board in which we can make and assign tasks throughout the team.
+This has helped to promote accountability as well as allow the better delegation of jobs.
+Finally, the last big productivity mechanism we implemented was the formation of a business/logistics subteam.
+This team has allowed the engineers to focus on engineering by acquiring money and organizing logistics, such as the trip to Atlanta.
+
+\subsection{Budget}
+The UT Aerospace Department was the first institution to support the team.
+TAR received a couple thousand dollars to begin our project as well as permission to use the aerospace facilities.
+After doing cost analysis TAR set the target budget at \$10,000.
+The team’s big break came after reaching out to Dr.
+Maruthi Akella.
+As well as providing the team with technical guidance, Dr.
+Akella introduced us to executives from corporations looking to sponsor student projects.
+Of the two corporations TAR reached out to General Dynamics Mission Systems (GDMS) decided us to fully sponsor us at the requested budget.
+The team is extremely grateful to have received the support of GDMS.
+Without this relationship, the development and trip to Atlanta would not have been possible.
+
 \section{Quadcopter}
+After our initial brainstorming period the team decided that the drone would would need to be able to easily interact with roombas, fly at least 10 min and have a large body to accommodate for the many electronics.
+At the beginning of our design process the team was faced with the prospects of buying, or designing and building a drone in house.
+After doing research, the design team decided that no prebuilt could fully meet the needs.
+The team decided to use the propeller guards as a forward blocking surface as well as a safety feature.
+To get the propeller guards to the required height to block the roobas the team chose to have the body of the drone be the landing gear.
+Surface area of the drone was elected to be maximized to decrease the precision needed to contact the top of the roombas.
+The quadcopter would be made with aluminum arms with a carbon fiber base to minimize weight and maximise strength and build quality.
+During build, we laser-cut wood for the base to allow for rapid iterating.
+Rapid iteration was instrumental in finding the optimal layout of electronics as well as flush out design flaws.
+Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions.
+The body of the drone was designed from the outset to keep the electronics easily accessible.
+For this reason a removable base cover was implemented.
+
 We decided to fabricate a quadcopter with aluminum arms with a carbon fiber base.
@@
 
+Both the optical flow sensor and the lidar sensor integrate with the Arducopter flight software that is running on the Pixhawk.
+The optical flow sensor is mounted on the side of the main body of the quadcopter to ensure that sensor receives adequate lighting at all times.
+
 \subsection{Vision}
 
-\subsection{Business}
+The drone tracks the roombas as well as keeps its global position using data taken from the camera mounted facing downwards.
+The Jetson Tx1 is what the drone uses to take the data from the camera and run our custom computer vision programs.
+We use the free OpenCV libraries to assist in our computer vision algorithms.
+
+In order to track the roombas, we opted to exploit the fact that the tops of the roombas are taped in either a distinct shade of red or green.
+This is done by applying a simple threshold and localizing the region in which the colored pixels are detected.
+With height input from the lidar, the computer vision algorithm can easily convert distance in pixels to distance in meters.
+This allows us to know the distances of the roombas relative to the drone.
+From here we can combine this data with our grid tracking algorithm and computational model to map the roombas globally.
+
+The algorithm for keeping the drone’s position within the grid relies on line detection.
+This is achieved by applying many operations to a standard RGB image.
+First, the image passes through the camera as an RGB picture.
+The image is then converted to grayscale.
+Next, the Canny Edge detection [1] filters the grayscale image into a binary image.
+From there, the binary image is fed through a Hough Transform [2] that essentially takes the binary image and outputs vectors which end up being the grid lines.
+The algorithm then reads these vectors and sorts them into two bins based off of the direction that they point [3].
+Once sorted, the closest vector in each group to the center of the image is found.
+The distance can be used to calculate distance within each grid square.
+Each time the center of the drone’s camera passes over a line, the grid square number is also updated.
+
+Below is a flowchart to illustrate our tracking algorithms: \\ \\ 
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
+     text centered, rounded corners, minimum height=2em]
+\tikzstyle{line} = [draw, -latex']
+\begin{tikzpicture}[node distance = 1.5cm, auto]
+    % Place nodes
+    \node [block] (camera) {Video camera captures frame};
+    \node [block, below of=camera] (passed) {Frame is passed into Jetson Tx1};
+    \node [block, below of=passed] (find) {Executable program finds locations of red and green blocks};
+    \node [block, below of=find] (calc) {Positioning program calculates drone location};
+    \node [block, below of=calc] (preferred) {Position and roomba locations allow drone to identify preferred target};
+    \node [block, below of=preferred] (passpreferred) {Preferred target is passed to Pixhawk};
+    \node [block, below of=passpreferred] (update) {Frame is updated and algorithm repeats};
+    % Draw edges
+    \path [line] (camera) -- (passed);
+    \path [line] (passed) -- (find);
+    \path [line] (find) -- (calc);
+    \path [line] (calc) -- (preferred);
+    \path [line] (preferred) -- (passpreferred);
+    \path [line] (passpreferred) -- (update);
+    \path [line] (update) -- ++(7cm,0) |- (camera);
+\end{tikzpicture}
 
@@
 \end{enumerate}
+
 \subsection{Kill Switch}
-Kill Switch
+Hopefully we will have a Kill Switch
 

### 2017-05-31 IARC_Paper/Paper.tex
Added images and flowchats oh boy

@@
 \usepackage{gensymb}
+\usepackage[section]{placeins}
 \usepackage{fancyhdr}
@@
 \usetikzlibrary{shapes,arrows}
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
+     text centered, rounded corners, minimum height=2em]
+\tikzstyle{line} = [draw, -latex']
 \usepackage{hyperref}
+\usepackage[belowskip=-50pt,aboveskip=2pt]{caption}
+% \setlength{\intextsep}{8pt plus 2pt minus 2pt}
 
@@
 Dr.
-Akella has been doring research to create agile intelligent quadrotors in environments free of GPS.
+Akella has been doing research to create agile intelligent quadrotors in environments free of GPS.
 Dr.
@@
 The winter break was used as a period of reflection.
-At the start of the new semester a new president was elected and a formal management style was implemented.
-Scrum.
+At the start of the new semester a new president was elected and a formal management style was implemented: Scrum.
 This is short term, agile style of management that makes short term goals and reflects and resets for the next “scrum”.
-Along with scrum, the team implemented organizational apps such as slack and trello.
+Along with scrum, the team implemented organizational apps such as Slack and Trello.
 Slack allowed the team to keep all the sub-team conversations separate, but unified.
 This kept members from silencing their line of communication as well as still allowing members to view what the other sub-teams are working on.
-Automated reminders for meetings were also set up through slack to prevent members from forgetting their duties to the team.
+Automated reminders for meetings were also set up through Slack to prevent members from forgetting their duties to the team.
 Trello was an incredible addition to our organizational platform.
@@
 Akella introduced us to executives from corporations looking to sponsor student projects.
-Of the two corporations TAR reached out to General Dynamics Mission Systems (GDMS) decided us to fully sponsor us at the requested budget.
+Of the two corporations TAR reached out to, General Dynamics Mission Systems (GDMS) decided to fully sponsor us at the requested budget.
 The team is extremely grateful to have received the support of GDMS.
@@
 \section{Quadcopter}
-After our initial brainstorming period the team decided that the drone would would need to be able to easily interact with roombas, fly at least 10 min and have a large body to accommodate for the many electronics.
+
+After our initial brainstorming period the team decided that the drone would would need to be able to easily interact with Roombas, fly at least 10 min and have a large body to accommodate for the many electronics.
 At the beginning of our design process the team was faced with the prospects of buying, or designing and building a drone in house.
@@
 The team decided to use the propeller guards as a forward blocking surface as well as a safety feature.
-To get the propeller guards to the required height to block the roobas the team chose to have the body of the drone be the landing gear.
-Surface area of the drone was elected to be maximized to decrease the precision needed to contact the top of the roombas.
-The quadcopter would be made with aluminum arms with a carbon fiber base to minimize weight and maximise strength and build quality.
+To get the propeller guards to the required height to block the Roombas the team chose to have the body of the drone be the landing gear.
+Surface area of the drone was elected to be maximized to decrease the precision needed to contact the top of the Roombas.
+The quadcopter would be made with aluminum arms with a carbon fiber base to minimize weight and maximize strength and build quality.
 During build, we laser-cut wood for the base to allow for rapid iterating.
@@
 
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[width=0.75\textwidth]{quad}
+\caption*{Quadcopter during testing phase}
+\end{center}
+\end{figure}
+
 \subsection{Hardware} 
@@
 
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[width=0.75\textwidth]{render}
+\caption*{SOLIDWORKS render of quadcopter}
+\end{center}
+\end{figure}
 \subsection{Controls}
@@
 
-Both the optical flow sensor and the lidar sensor integrate with the Arducopter flight software that is running on the Pixhawk.
+Both the optical flow sensor and the LIDAR sensor integrate with the Arducopter flight software that is running on the Pixhawk.
 The optical flow sensor is mounted on the side of the main body of the quadcopter to ensure that sensor receives adequate lighting at all times.
-
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
+    % Place nodes
+    \node [block] (battery) {Battery};
+    \node [block, below of=battery] (siphon) {Power siphon};
+    \node [block, below of=siphon] (Pixhawk) {Pixhawk};
+    \node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
+    \node [block, below left of=battery, xshift=-3cm] (Jetson) {Nvidia Jetson TX1};
+    \node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
+    \node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
+    \node [block, below of=Jetson] (Camera) {Camera};
+    \node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
+    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spectrum) {Spectrum controller};
+    \node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
+    \node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
+    % Draw edges
+    \path [line] (battery) -- (siphon);
+    \path [line] (siphon) -- (Pixhawk);
+    \path [line] (battery) -- (PDB);
+    \path [line] (PDB) -- (ESCs);
+    \path [line] (battery) -- (Jetson);
+    \path [line] (Camera) -- (Jetson);
+    \path [line, dashed] (Flow) -- (Pixhawk);
+    \path [line, dashed] (Jetson) -- (Pixhawk);
+    \path [line, dashed] (LIDAR) -- (Pixhawk);
+    \path [line, dashed] (Pixhawk) -- (Telemetry);
+    \path [line, dashed] (Spectrum) -- (Pixhawk);
+    \path [line, dashed] (Pixhawk) -- (ESCs);
+    \path [line] (ESCs) -- (Motors);
+\end{tikzpicture}
+\caption*{Solid arrows indicate power while dashed lines indicate power+data}
+\end{center}
+\end{figure}
 \subsection{Vision}
 
-The drone tracks the roombas as well as keeps its global position using data taken from the camera mounted facing downwards.
-The Jetson Tx1 is what the drone uses to take the data from the camera and run our custom computer vision programs.
+The drone tracks the Roombas as well as keeps its global position using data taken from the camera mounted facing downwards.
+The Jetson TX1 is what the drone uses to take the data from the camera and run our custom computer vision programs.
 We use the free OpenCV libraries to assist in our computer vision algorithms.
 
-In order to track the roombas, we opted to exploit the fact that the tops of the roombas are taped in either a distinct shade of red or green.
+In order to track the Roombas, we opted to exploit the fact that the tops of the Roombas are taped in either a distinct shade of red or green.
 This is done by applying a simple threshold and localizing the region in which the colored pixels are detected.
-With height input from the lidar, the computer vision algorithm can easily convert distance in pixels to distance in meters.
-This allows us to know the distances of the roombas relative to the drone.
-From here we can combine this data with our grid tracking algorithm and computational model to map the roombas globally.
+With height input from the LIDAR, the computer vision algorithm can easily convert distance in pixels to distance in meters.
+This allows us to know the distances of the Roombas relative to the drone.
+From here we can combine this data with our grid tracking algorithm and computational model to map the Roombas globally.
 
@@
 Below is a flowchart to illustrate our tracking algorithms: \\ \\ 
-\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
-     text centered, rounded corners, minimum height=2em]
-\tikzstyle{line} = [draw, -latex']
 \begin{tikzpicture}[node distance = 1.5cm, auto]
@@
     \node [block] (camera) {Video camera captures frame};
-    \node [block, below of=camera] (passed) {Frame is passed into Jetson Tx1};
+    \node [block, below of=camera] (passed) {Frame is passed into Jetson TX1};
     \node [block, below of=passed] (find) {Executable program finds locations of red and green blocks};
     \node [block, below of=find] (calc) {Positioning program calculates drone location};
-    \node [block, below of=calc] (preferred) {Position and roomba locations allow drone to identify preferred target};
+    \node [block, below of=calc] (preferred) {Position and Roomba locations allow drone to identify preferred target};
     \node [block, below of=preferred] (passpreferred) {Preferred target is passed to Pixhawk};
@@
 
+\begin{center}
+\includegraphics[width=0.8\textwidth]{tracking}
+\end{center}
+
 \section{Safety}
-\subsection{Pre-flight Checklist}
+\subsection{Preflight Checklist}
 \begin{enumerate}
@@
 
+\begin{center}
+\includegraphics[width=0.8\textwidth]{Selection_004}
+\end{center}
+
 To simulate the quadcopter, we use Ardupilot's Software in the Loop (SITL) simulation method to run a Gazebo simulation with ROS.
@@
 \section{Acknowledgments}
-We are thankful for Dr. Akela at UT Austin. Additionally, we are thankful for UT Austin's Aerospace Department for providing us with a meeting room and sponsorship.
+We are thankful for Dr. Akella at UT Austin. Additionally, we are thankful for UT Austin's Aerospace Department for providing us with a meeting room and sponsorship.
 

### 2017-05-31 IARC_Paper/Paper.tex
Add pictures and flowcharts oh boy
Fix some things that were missing

@@
 Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017.
-Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a camera (put name here) for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
+Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a Logitech C210 camera for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
 The mission takes place in a GPS denied environment, so gridlines will be used as reference positions.
@@
 Mission 7a of IARC consists of developing an aerial vehicle that can interact with moving ground robots.
-Those ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions.
+These ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions.
 The vehicle must herd the 10 Roombas across one side of the 20 meter by 20 meter grid.
@@
 \subsection{Hardware} 
-At the end of the aluminum arms sit four (insert here) motors for lift.
-The four motors provide (insert) grams of lift, a sufficient amount for our (insert) gram quadcopter.
+At the end of the aluminum arms sit four Tiger MT2216 v2 motors with 12in plastic props for lift.
+The four motors provide 2.25 kilograms of lift at 65\% throttle, a sufficient amount for our sightly under 2 kilogram quadcopter.
 The arms are fixed into the base pieces, which do not pass enough vibration to the sensors that we needed any additional vibration damping.
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{render}
+\includegraphics[width=1\textwidth]{render}
 \caption*{SOLIDWORKS render of quadcopter}
@@
     \node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
-    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spectrum) {Spectrum controller};
+    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
     \node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
@@
     \path [line, dashed] (Pixhawk) -- (Telemetry);
-    \path [line, dashed] (Spectrum) -- (Pixhawk);
+    \path [line, dashed] (Spektrum) -- (Pixhawk);
     \path [line, dashed] (Pixhawk) -- (ESCs);

### 2017-05-31 IARC_Paper/Paper.tex
Take out kill switch because Samid said so
Profread paper

@@
 \usepackage{hyperref}
-\usepackage[belowskip=-50pt,aboveskip=2pt]{caption}
+\usepackage[belowskip=-22pt,aboveskip=2pt]{caption}
 % \setlength{\intextsep}{8pt plus 2pt minus 2pt}
@@
 Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017.
-Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a Logitech C210 camera for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter.
+Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a Logitech C210 camera for vision, a Nvidia Jetson TX1 for vision processing, and a Pixhawk for controlling the quadcopter.
 The mission takes place in a GPS denied environment, so gridlines will be used as reference positions.
@@
 These ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions.
-The vehicle must herd the 10 Roombas across one side of the 20 meter by 20 meter grid.
+The vehicle must herd the 10 Roombas across one side of the 20 by 20 square meter grid.
 Additionally, 4 obstacle Roombas have PVC poles the vehicle must avoid.
@@
 
-An added difficulty to the mission is that the setting is a (Global Positioning System) GPS denied environment.
+An added difficulty to the mission is that the setting is a Global Positioning System (GPS) denied environment.
 Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid.
@@
 
-\subsection{Yearly milestones}
-This is the first time Texas Aerial Robotics is competing in any event. Our goal for the year was to be competitive at this year's IARC.
+\subsection{Yearly Milestones}
+This is the first time Texas Aerial Robotics is competing in any event. Our goal for the year was to be competitive at this year's IARC. %Add more here
 
@@
 At the beginning of the creation of Texas Aerial Robotics, the team searched for professors to provide technical guidance for the project.
-Within the UT Department of Aerospace TAR reached out to Dr.
-Maruthi Akella.
+TAR reached out to Dr.
+Maruthi Akella, a professor at UT Austin's Aerospace Engineering Department.
 Dr.
@@
 From the outset of the relationship Dr.
-Akella has provided expertise, access to his grad students as well as access to his indoor and outdoor lab.
+Akella has provided expertise, access to his grad students, as well as access to his indoor and outdoor lab.
 Dr.
-Akella also introduced us to multiple corporation looking to sponsor student projects.
+Akella also introduced us to multiple corporations looking to sponsor student projects.
 TAR is incredibly thankful to have the support of Dr.
@@
 As important as the drone a team develops, is the process in which it is developed.
-The past year has been Texas Aerial Robotics(TAR) maiden year and the team has put a lot of effort in developing the process to catalyze the engineering of the drone.
+The past year has been Texas Aerial Robotics (TAR) maiden year, and the team has put a lot of effort in developing the process to catalyze the engineering of the drone.
 During the fall semester, the team made just about every mistake in the book with regards to how to run a competition team.
@@
 At the start of the new semester a new president was elected and a formal management style was implemented: Scrum.
-This is short term, agile style of management that makes short term goals and reflects and resets for the next “scrum”.
+This is an agile style of management that makes short term goals and reflects and resets for the next “scrum”.
 Along with scrum, the team implemented organizational apps such as Slack and Trello.
@@
 
-After our initial brainstorming period the team decided that the drone would would need to be able to easily interact with Roombas, fly at least 10 min and have a large body to accommodate for the many electronics.
+After our initial brainstorming period the team decided that the drone would need to be able to easily interact with Roombas, fly at least 10 minutes and have a large body to accommodate for the many electronics.
 At the beginning of our design process the team was faced with the prospects of buying, or designing and building a drone in house.
-After doing research, the design team decided that no prebuilt could fully meet the needs.
+After doing research, the design team decided that no prebuilt quadcopter could fully meet the needs.
 The team decided to use the propeller guards as a forward blocking surface as well as a safety feature.
@@
 
-We decided to fabricate a quadcopter with aluminum arms with a carbon fiber base.
-During build, we laser-cut wood for the base to allow for rapid iterating.
-Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions.
-Our quadrotor needed to house all of the sensors for operation with sufficient flight time.
-
 \begin{figure}[!htbp]
@@
 
-\subsection{Hardware} 
+% \subsection{Hardware} 
 At the end of the aluminum arms sit four Tiger MT2216 v2 motors with 12in plastic props for lift.
@@
     \path [line] (battery) -- (Jetson);
-    \path [line] (Camera) -- (Jetson);
+    \path [line, dashed] (Camera) -- (Jetson);
     \path [line, dashed] (Flow) -- (Pixhawk);
@@
 \end{tikzpicture}
-\caption*{Solid arrows indicate power while dashed lines indicate power+data}
+\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
 \end{center}
@@
 
-\subsection{Kill Switch}
-Hopefully we will have a Kill Switch
+% \subsection{Kill Switch}
+% Hopefully we will have a Kill Switch
 
@@
 We wanted a design that would not interfere with the prop wash, but still be able to avoid the quadcopter from destroying itself in the unfortunate event it collides with something.
-The first iteration looked nice, but interfered with the prop wash too much and weighted too much, reducing the thrust.
+The first iteration looked nice, but interfered with the prop wash too much and weighed too much, reducing the thrust.
 

### 2017-05-31 IARC_Paper/Paper.tex
Some content changes. Possibily final version.

@@
 \section{Conclusion}
-We still have quite a ways to go before we can consider ourselves competitive.
-Due to the fact that we started our organization in 2017, we have come a long way and learned a lot, yet we plan to continue work to beat this mission as quick as possible.
-Hopefully we do well at Georgia Tech!
+Last year, Texas Aerial Robotics was a mere idea in the minds of the student engineers participating today.
+Because of the incredible drive of the founding members, TAR will have a solid showing at the competition in July.
+Not only has the team risen to the engineering challenge, they have built a sustainable team that is rooted in the engineering process and will allow TAR to expand in the coming years.
+All of the current members will be returning next year to further develop their knowledge and understanding of engineering and technology as well as spread their vision of drone technology to other students at UT Austin.
 

### 2017-05-31 IARC_Paper/Paper.tex
Add risk reduction section

@@
 Thus, we determined that we needed to design other methods to determine our positioning.
-By using a camera to observe the gridlines and an Inertial Measurement Unit (IMU), we are working our way to determining where the vehicle is on the grid.
+Our conceptional solution is to use a camera to observe the gridlines and an Inertial Measurement Unit (IMU) to determine where the vehicle is on the grid.
+Once we know that, we can have a computer vision program identify ground robots at risk of leaving the field.
 
@@
 
+\subsection{Risk Reduction}
+We took significant steps to ensure safe operation of the quadcopter.
+In order to keep the quadcopter from flying where we do not want, we have a Spektrum receiver module onboard so our designated pilot can manually control the vehicle.
+Additionally, we are able to check the status of the quadcopter through our telemetry to our ground station.
+The PX4 flight stack helps keep interference risk down through the EMI calibration on the Pixhawk.
+Additionally, logs from the Pixhawk showed us that vibration on the built quadcopter was well within recommended amounts.
+
 \subsection{Prop Guards}

### 2018-05-31 IARC_Paper_2018/Paper.tex
added a couple more sections

\documentclass[12pt,letterpaper]{article}

\usepackage{graphicx,
			amssymb,
			amsmath,
			titlesec,
			lipsum,
			setspace,
			lastpage,
			fancyhdr,
			tikz,
			titling}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [rectangle, draw, fill=blue!20,
     text centered, rounded corners, minimum height=2em]
\tikzstyle{line} = [draw, -latex']

%% Figure caption formatting
\usepackage[labelfont=it,textfont=it,labelsep=period]{caption}
\usepackage[labelfont=it,textfont=it,labelsep=period]{subcaption}

%% Overall margins
\usepackage[margin=1in]{geometry}

%% Footer formatting
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\cfoot{\textbf{\textsf{Page\ \thepage\ of \pageref{LastPage}}}}

%% Author list formatting
\newenvironment{nscenter}
 {\parskip=0pt\par\nopagebreak\centering}
 {\par\noindent\ignorespacesafterend}

\newcommand{\affiliatedauthor}[2]{
\begin{nscenter}
	#1 \\ \textit{#2}
\end{nscenter}
}

%% Abstract formatting
\renewcommand{\abstractname}{ABSTRACT}

\renewenvironment{abstract}
 {\vspace{-0.5ex}
	\small
	\begin{center}
		\bfseries \abstractname\vspace{-4ex}\vspace{0pt}
	\end{center}
	\list{}{
		\setlength{\leftmargin}{0.5in}
		\setlength{\rightmargin}{\leftmargin}
	}
	\item\relax}
 {\endlist}

%% Section header formatting
\renewcommand\thesection{}
\renewcommand\thesubsection{}
\renewcommand\thesubsubsection{}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\itshape}{\thesubsubsection}{1em}{}
\titlespacing*{\section}{0pt}{2ex}{-1.5ex}
\titlespacing*{\subsection}{0pt}{2ex}{-1.5ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-1.5ex}

%% Paragraph formatting (changing this messes with literally everything)
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex}
\newcommand\tab[1][1cm]{\hspace*{#1}}

%%%%%%%%%%%%%%%%%%%%%% ADD TITLE HERE %%%%%%%%%%%%%%%%%%%%%%
\title{Intelligent Quadcopter for IARC 2018}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
	\textbf{\LARGE{\thetitle}}
\end{center}

%%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
\affiliatedauthor{Noel Brownback}{The University of Texas at Austin}
\affiliatedauthor{Anthony Carreon}{The University of Texas at Austin}
\affiliatedauthor{Shayer Hassan}{The University of Texas at Austin}
\affiliatedauthor{Eric Johnson}{The University of Texas at Austin}
\affiliatedauthor{Colin Lewis}{The University of Texas at Austin}
\affiliatedauthor{Mark Loveland}{The University of Texas at Austin}
\affiliatedauthor{Umer Salman}{The University of Texas at Austin}
\affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7. A combination of lightweight materials and powerful propulsion enables optimizes flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand. This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft. Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% MAIN TEXT %%%%%%%%%%%%%%%%%%%%%%

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

	Texas Aerial Robotics addresses these challenges by utilizing computer vision. Through computer vision the drone has the ability to both understand its location, and also track targets in real time. The drone records the data and position of the objects, simulating those which lie beyond the field of view, which allows for strategic analysis and definition based on estimates of unseen/out of sight targets. Interaction with these objectives is achieved using the carbon fiber bottom plate of the aircraft and perimeter prop guards, a material choice that lends itself to lightweight resiliency.

	Yearly Objectives:
	2017 - Have a working bot, with computer vision software in working or nearly working
	2018 - Continue development of computer vision, develop a computational  game strategy through creation of simulations of the motion of roombas, tweak the physique of the drone for better flight control and stability

\section*{Air Vehicle}
	\subsection*{Propulsion and Lift System}
	        The vehicle utilizes a x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omni-directional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 kg weight to maintain a 2.2 thrust-to-weight ratio ideal for battery life and flight time. 
			The propellers used with the motors are 13 [in] long and made of carbon fiber. These T-Motor propellers provide excellent precision, durability, and efficiency. The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.

	\subsection*{Guidance, Navigation, and Control}
		\subsubsection*{Stability Augmentation System}
			Our system builds off of the robust open source project Arducopter.  Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LIDAR and the optical flow sensor. The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.  The vast community of developers and users ensures refined controls code with lots of features.

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin.  This has been done to allow our drone to navigate in GPS denied environments.  For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the  IMU, compass, altitude LIDAR and the optical flow sensor. The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2d lidar. The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination. Over time, the EKF will have error in comparison to reality. To combat this, the control node will input a correction vector.  This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows. Gaussian blur, color threshold, erosion, dilation, Hough, line intersection, and non maximum suppression.

		\begin{figure}[!htbp]
		\begin{center}
		\includegraphics[width=0.75\textwidth]{system}
		\caption*{Overview of control system}
		\end{center}
		\end{figure}

		% \begin{figure}[!htbp]
		% 	\begin{center}
		% 		\begin{tikzpicture}[node distance = 3cm, auto]
		% 			% Place nodes
		% 			\node [block] (IMU) {IMU + Flow};
		% 			\node [block, below of=IMU] (Camera) {Camera};
		% 			\node [block, right of=IMU] (EKF) {EKF};
		% 			\node [block, below of=EKF] (Vision) {Vision};
		% 			\node [block, below right of=EKF] (Strategy) {Strategy};
		% 			\node [block, below right of=Strategy] (2DLIDAR) {2D LIDAR};
		% 			\node [block, right of=Strategy] (mavros) {mavros};
		% 			\node [block, right of=mavros] (Pixhawk) {Pixhawk};
		% 			\node [block, right of=Pixhawk] (Move) {Move};
		% 			% Draw edges
		% 			\path [line] (IMU) -- (EKF);
		% 			\path [line] (Camera) -- (Vision);
		% 			\path [line] (EKF) -- (Strategy);
		% 			\path [line] (Vision) -- (Strategy);
		% 			\path [line] (2DLIDAR) -- (Strategy);
		% 			\path [line] (2DLIDAR) -- (mavros);
		% 			\path [line] (Strategy) -- (mavros);
		% 			\path [line] (mavros) -- (Pixhawk);
		% 			\path [line] (Pixhawk) -- (Move);
		% 		\end{tikzpicture}
		% 		\caption*{Overview of control system}
		% 	\end{center}
		% \end{figure}

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch. In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone’s systems.

\section*{Payload}
	The Drone has been designed to carry all the necessary GNC sensors, 2d LIDAR, and array of cameras and 3 nvidia TX2 Jetsons. In addition the drone carries a telemetry radio, kill switch and rc receiver in order to carry out safe flight. 
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
    		The 1-D LiDAR module used is the LiDAR-lite v3 from Garmin. This one dimensional sensor is directed downwards and provides data that is used to determine altitude. The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring distance travelled and direction. The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses. The data from these sensors is used by the Pixhawk onboard system for flight control and the maneuvering of the quadcopter.

		\subsubsection*{Mission Sensors}
			For the goal of completing Mission 7 the drone must be able to detect roombas and obstacles. The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
			The singular bottom camera is a Logitech C210 webcam. This webcam is used for roomba detection and tracking the targeted roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270. These are used to recognize and track the roombas around the playing field. These five webcams provides enough information allowing the drone to incorporate the recognized roombas into the strategy of the autonomous system. 
			The 2D LiDAR sensor is the SWEEP sensor by Scanse.This is a single lidar that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

		\subsection*{Target Identification}
			For target identification, the drone carries five Logitech C270 USB webcams. One of the cameras is located at the bottom of the drone and faces straight downward. The other four cameras are mounted on the bottom side of each arm facing outward. All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.

			There are two main objectives that need to be completed to successfully relay target information to the strategy node. The first objective is to take in the raw video data and detect the target Roombas so that pixel numbers of the centroids of the Roombas in the frame can be sent as output. The second objective is to take the pixel numbers of the centroids of the detected Roombas as input, and then output x and y coordinates relative to the drone using a coordinate transformation and the known height and orientation of the camera with respect to the floor.

			In order to accomplish the first objective, an open source software package developed by Joseph Redmon called YOLO (You Only Look Once) is used. More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher frame rates. YOLO is a neural network that can identify user-defined objects once it has been trained. After training the neural network by feeding in approximate 2000 photos of the target Roombas (with the Roombas identified manually), YOLO can reliably identify target Roombas in real time. An example is displayed below:

			% \begin{figure}[!htbp]
			% 	\begin{center}
			% 		\includegraphics[width=0.75\textwidth]{RoombaDetectionImage}
			% 	\end{center}
			% \end{figure}

			After YOLO outputs the pixel locations of each identified target Roomba, the final objective is to transform these pixel coordinates into x-y coordinates relative to the drone. In addition to the pixel coordinate (PIX \#), the other knowns are height ($z$), camera rotation angle relative to downward facing ($\theta$), and field of view ($\phi$), as well as total pixels in x and y (PIX\_MAX).  Here is a diagram to illustrate these knowns below:

			\begin{tikzpicture}[scale=3]
				\coordinate [label=left:$X$] (X) at (-1.5cm,-1cm);
				\coordinate [label=right:$Y$] (Y) at (1.5cm,-1cm);
				\coordinate [label=above:$Z$] (Z) at (-1.5cm,1cm);
				\coordinate (phi) at (.1cm,-1cm);
				\coordinate (theta) at (-.75cm,-1cm);
				\draw[<->] (Z) -- node[below] {} (X) -- node[right] {} (Y);
				\draw[dashed](Y) -- node[above left] {} (Z);
				\draw[dashed] (Z) -- node[below] {} (phi);
				\draw[dashed] (Z) -- node[below] {} (theta);
				\tkzMarkRightAngle[draw=black](Z,X,Y)
				\tkzDrawPoints[color=black,fill=white](X)
				\tkzMarkAngle[size=1cm,color=cyan](X,Z,phi)
				\tkzMarkAngle[size=1.5cm,color=cyan](theta,Z,Y)
				\tkzLabelAngle[dist=1.6cm](theta,Z,Y){$\phi$}
				\tkzLabelAngle[dist=1.1cm](X,Z,phi){$\theta$}
			\end{tikzpicture}

			In order to transform this pixel coordinate into x-y coordinates relative to the drone, a few key assumptions made are that:

				\begin{itemize}
					\item The camera behaves as a pinhole model
					\item Each pixel in the frame takes up an approximately equal fraction of the field of view
				\end{itemize}

			A big pitfall in this model is that no distortion from the camera lens is accounted for; these effects are still being investigated.

				\textbf{Transformation}:

				Pixel given from YOLO: $PIX$ Pixel number of the center:

				\begin{align*}
				PIX = \frac{PIX\_MAX}{2}
				\end{align*}

				Define $\phi$ as portion of angle from center image to pixel detected:

				\begin{align*}
				\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})
				\end{align*}

				To find the real coordinate ($REAL$) relative to the drone in the $X$ direction, There are two cases:

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:

						\begin{align*}
						REAL = z * tan(\theta + \frac{\phi}{2})
						\end{align*}

						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:

						\begin{align*}
						REAL = z * tan(\theta - \frac{\phi}{2})
						\end{align*}

				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$

						\begin{align*}
						REAL = z * tan(\theta - \frac{\phi}{2})
						\end{align*}

						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$

						\begin{align*}
						REAL = z * tan(\theta + \frac{\phi}{2})
						\end{align*}

				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.

		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the ‘gym reference frame’. The gym reference frame is defined as a right handed coordinate system starting in the bottom left hand corner of the field where the green line meets the outer white line. This transformation is defined as followed.

		\begin{align*}
		yawAngle = currentHeading - GymOffset
		\end{align*}
		\begin{align*}
		roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone 
		\end{align*}
		\[
		R(3) = 
			\begin{bmatrix}
			cos(yawAngle) & -sin(yawAngle) & 0 \\
			sin(yawAngle) & cos(yawAngle)  & 0 \\
			0 & 0 & 1 
			\end{bmatrix}
		\]

		CR is the correction vector formulated from the corner detection vision algorithm. EKFdronePose is the position of the drone queried from the pixhawk. R(3) is the rotation matrix about the third axis. GymOffset is the direction of the 2 axis defined during the startup sequence before flight. The new coordinate in the gym frame is passed off to the strategy node as data to be acted on. 
	\subsection*{Threat Avoidance}
		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle roombas. This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target roombas. The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.

	\subsection*{Communications}
		On the Jetsons data is passed between software nodes via ROS. Data in between our multiple Jetsons is passed via ros messages through direct ethernet connections. Commands to flight commuter are passed via serial connection with data encoded in MAVLINK messages.

	\subsection*{Power Management System}
		The quadcopter uses  a 10000mAh 4S 10C LiPo battery and a 2000mAh 3S 15C LiPo battery for power. The 10000mAh 4S 10C LiPo is used to power our ESCs and Motors. With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 grams of thrust per motor needed for hovering flight. The 2000mAh 3S 15C LiPo will power the flight control board and Jetson compute units.
		\begin{align*}
		T(min)=Battery power(AH)*60/Total current drawn by motors
		\end{align*}
		Assuming an average throttle of 65\% for maneuvering, we see a 9 A current draw from each motor, and with a 10 Ah battery, that provides us with 16 minutes of flight time with minimal maneuvering and height change. This gives us plenty of headroom for more intense altitude and positioning changes, which will allow us to move more quickly during the competition, a valuable asset with the given time limitation. 
		\begin{align*}
		Max continuous Amp draw (A) = Battery capacity (Ah) * Discharge rate (C)
		\end{align*}
		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 A and maximum practical current draw of 19.4 A required by the motors. The 10000 mAh battery with a 10C discharge rate gives us a maximum continuous current draw of 100 A, matching the limit of the motors.

		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above-10 minute flight times at speeds below 15 mph

		INSERT GRAPH

		As for the 2000 mAh 3S battery, this battery powers our Pixhawk flight controller and our three Jetson TX2 compute units. This was done partly to dedicate the entirety of the main battery to propulsion to maximize flight time. The other reason is that the speed controllers we chose (T-motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution. 2000 mAh was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LIDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

\section*{Risk Reduction}
	\subsection*{Vehicle Status}
		\subsubsection*{Shock/Vibration Isolation}
		The modern pixhawk flight controller contains internal damping from the vibration of the drone’s structure. The decided there is no need for extra damping. After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts. The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognise landing. Because of this, nominal landings will not interfere with the guidance or navigation of the drone.

		\subsubsection*{EMI/RFI Solutions}
		The Arducopter flight stack helps keep interference risk down through the EMI calibration on the Pixhawk. The calibration calculates the magnetic interference correction by formulating a function of the magnetic interference based on the power setting of the motors.

	\subsection*{Safety}
		We took significant steps to ensure safe operation of the quadcopter. In order to keep the quadcopter from flying where we do not want, we have a Spektrum receiver module onboard so our designated pilot can manually control the vehicle. Additionally, we are able to check the status of the quadcopter through our telemetry to our ground station. The structure of the drone is also outfitted with prop guards to mitigate damage to people or property in the event of catastrophic failure. Our prop guards took multiple iterations. We wanted a design that would not interfere with the prop wash, but still be able prevent damage to the quadcopter itself in the unfortunate event of collision. The first iteration looked nice, but interfered with the prop wash too much and weighed too much, reducing the thrust. However, the next iteration cut weight and did not interfere with the prop wash.

	\subsection*{Modeling and Simulation}

		To safely test our software throughout the development process, the team implemented a simulation using the Gazebo application. Using this tool, TAR was able to deploy full scale software in the loop simulation without jeopardizing hardware with each design iteration.

    	To employ the Gazebo framework, the team imported a standard quadcopter model from the arducopter standard library and roomba models from Gazebo model library, which were then updated with the color coded plates and obstacle tubes prescribed for the competition. Additionally, the ground plain within the reproduction was changed to match the texture expected at the competition.

		Gazebo was chosen because of its compatibility with ROS and Ardupilot, the internal communication protocol employed onboard our drone. With this congruence, the exact same software run onboard the drone could be run within the simulation, complete with sensor feedback detected within the simulated instance.  C++ scripts could then be utilized to enforce the correct roomba behaviors, scripting the robots using the same messaging environment as the quadcopter itself (ROS).

		Overall, modeling our software behavior within a Gazebo simulation greatly expedited the development process. By standardizing the simulation setup, tests could be conducted on multiple computers at any time, instead of requiring sluggish process of updating, calibrating, and flying the physical drone. Additionally, simulation protected the hardware from the accidents and unintentional flight behavior inherent to prototype software.

	\subsection*{Testing}
		Simulation, however, can only prove so much. Eventually, refined software was tested on a model testbed or on the drone itself. Much of the computer vision and general software integration was developed on this testbed, where performance could be verified with the same sensors and computational hardware as the aircraft before full scale deployment. Even strategy nodes could be tested on this platform, with waypoint predictions vetted before being deployed to the aircraft.

    	Flight tests, expectedly, require a specific setting. Generally, Texas Aerial Robotics tested on the roof of the Aerospace building on campus at the The University of Texas. This controlled environment bore witness to hardware implementation throughout our design process, from original flight readiness to early autonomy.

		However, summer development saw additional test flights conducted in a vacant parking garage, but both locations suffered from magnetic inconsistencies which interfered with compass calibrations. Because of this, later tests, including the qualifying run submitted, were conducted in a parking lot to the north of the university.

		Regardless of the setting, each flight test was conducted with constant apparatus. A four meter by four meter test mat printed with the pattern expected at competition, to allow optical flow for navigation. Across this mat drives a test roomba, which accurately recreates both the physical appearance and behaviors of those robots that will be tracked at the venue, complete with top plate and switch. Finally, there is the drone itself, which starts on a corner of the mat, takes off autonomously, and then executes the maneuver to be tested.

\section*{Conclusion}
		Texas Aerial Robotics’ solution to the challenges provided by IARC mission 7 are bountiful and diverse. The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success, Unique software utilizes input from an expansive battery of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area. Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
	\nocite{redmon2016yolo9000}
	\bibliography{bibliography}
	\bibliographystyle{plain}

\end{document}

### 2018-05-31 IARC_Paper_2018/Paper.tex
fixed more stuff

@@
 Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7.
-A combination of lightweight materials and powerful propulsion enables optimizes flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand.
+A combination of lightweight materials and powerful propulsion enables optimized flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand.
 This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft.
@@
 
-	Yearly Objectives:
+	\begin{figure}[!htbp]
+	\begin{center}
+	\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
+	    % Place nodes
+	    \node [block] (battery) {Battery};
+	    \node [block, below of=battery] (siphon) {Power siphon};
+	    \node [block, below of=siphon] (Pixhawk) {Pixhawk};
+	    \node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
+	    \node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
+	    \node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
+	    \node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
+	    \node [block, below right of=Jetson] (Camera) {Cameras};
+	    \node [block, below left of=Jetson] (2dLidar) {2D LiDAR};
+	    \node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
+	    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
+	    \node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
+	    \node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
+	    % Draw edges
+	    \path [line] (battery) -- (siphon);
+	    \path [line] (siphon) -- (Pixhawk);
+	    \path [line] (battery) -- (PDB);
+	    \path [line] (PDB) -- (ESCs);
+	    \path [line] (battery) -- (Jetson);
+	    \path [line, dashed] (Camera) -- (Jetson);
+	    \path [line, dashed] (2dLidar) -- (Jetson);
+	    \path [line, dashed] (Flow) -- (Pixhawk);
+	    \path [line, dashed] (Jetson) -- (Pixhawk);
+	    \path [line, dashed] (LIDAR) -- (Pixhawk);
+	    \path [line, dashed] (Pixhawk) -- (Telemetry);
+	    \path [line, dashed] (Spektrum) -- (Pixhawk);
+	    \path [line, dashed] (Pixhawk) -- (ESCs);
+	    \path [line] (ESCs) -- (Motors);
+	\end{tikzpicture}
+	\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
+	\end{center}
+	\end{figure}
+
+	\subsection{Yearly Milestones}
 	2017 - Have a working bot, with computer vision software in working or nearly working

### 2018-05-31 IARC_Paper_2018/Paper.tex
added canny
More paper working stuff

@@
 \usepackage{tkz-euclide}
+\usepackage{setspace}
+
 \usetkzobj{all}
@@
 text centered, rounded corners, minimum height=2em]
+
 \tikzstyle{line} = [draw, -latex']
+\newenvironment{my_enumerate}{
+	\begin{enumerate}
+	\setlength{\itemsep}{1pt}
+	\setlength{\parskip}{0pt}
+	\setlength{\parsep}{0pt}}{\end{enumerate}
+}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%% ADD TITLE HERE %%%%%%%%%%%%%%%%%%%%%%
 \title{Intelligent Quadcopter for IARC 2018}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7.
-A combination of lightweight materials and powerful propulsion enables optimized flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand.
+A combination of lightweight materials and powerful propulsion enables optimizes flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand.
 This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft.
@@
 
-\section*{INTRODUCTION}
+\section*{Introduction}
 	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone.
 Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone.
-Thus, mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden.
+Thus, Mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden.
 Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.
@@
 	2017 - Have a working bot, with computer vision software in working or nearly working
-	2018 - Continue development of computer vision, develop a computational  game strategy through creation of simulations of the motion of roombas, tweak the physique of the drone for better flight control and stability
+	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability
 
@@
 This is necessary for our 3.15 kg weight to maintain a 2.2 thrust-to-weight ratio ideal for battery life and flight time.
+
 			The propellers used with the motors are 13 [in] long and made of carbon fiber.
@@
 This algorithm goes as follows.
-Gaussian blur, color threshold, erosion, dilation, Hough, line intersection, and non maximum suppression.
+Gaussian blur, color threshold, erosion, dilation, Canny, Hough, line intersection, and non maximum suppression.
 
@@
 			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch.
-In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone’s systems.
+In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.
 
@@
 The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
+
 			The 1-D LiDAR module used is the LiDAR-lite v3 from Garmin.
@@
 		\subsubsection*{Mission Sensors}
-			For the goal of completing Mission 7 the drone must be able to detect roombas and obstacles.
+			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles.
 The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
 			The singular bottom camera is a Logitech C210 webcam.
-This webcam is used for roomba detection and tracking the targeted roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270.
-These are used to recognize and track the roombas around the playing field.
-These five webcams provides enough information allowing the drone to incorporate the recognized roombas into the strategy of the autonomous system.
+This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270.
+These are used to recognize and track the Roombas around the playing field.
+These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
 			The 2D LiDAR sensor is the SWEEP sensor by Scanse.This is a single lidar that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection.
@@
 
-			% \begin{figure}[!htbp]
-			% 	\begin{center}
-			% 		\includegraphics[width=0.75\textwidth]{RoombaDetectionImage}
-			% 	\end{center}
-			% \end{figure}
+			\begin{figure}[!htbp]
+				\begin{center}
+					\includegraphics[width=0.75\textwidth]{roomba}
+				\end{center}
+			\end{figure}
 
@@
 
+			\begin{spacing}{.2}
 			In order to transform this pixel coordinate into x-y coordinates relative to the drone, a few key assumptions made are that:
@@
 
-				\begin{align*}
-				PIX = \frac{PIX\_MAX}{2}
-				\end{align*}
+				\begin{center}
+					$PIX = \frac{PIX\_MAX}{2}$
+				\end{center}
 
@@
 
-				\begin{align*}
-				\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})
-				\end{align*}
+				\begin{center}
+					$\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
+				\end{center}
 
@@
 						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:
+						\begin{center}
+							$REAL = z * tan(\theta + \frac{\phi}{2})$
+						\end{center}
+						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:
+						\begin{center}
+							$REAL = z * tan(\theta - \frac{\phi}{2})$
+						\end{center}
+				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
+						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$
+						\begin{center}
+							$REAL = z * tan(\theta - \frac{\phi}{2})$
+						\end{center}
+						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$
+						\begin{center}
+							$REAL = z * tan(\theta + \frac{\phi}{2})$
+						\end{center}
+				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
+			\end{spacing}
 
-						\begin{align*}
-						REAL = z * tan(\theta + \frac{\phi}{2})
-						\end{align*}
-
-						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:
-
-						\begin{align*}
-						REAL = z * tan(\theta - \frac{\phi}{2})
-						\end{align*}
-
-				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
-
-						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$
-
-						\begin{align*}
-						REAL = z * tan(\theta - \frac{\phi}{2})
-						\end{align*}
-
-						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$
-
-						\begin{align*}
-						REAL = z * tan(\theta + \frac{\phi}{2})
-						\end{align*}
-
-				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
-
-		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the ‘gym reference frame’.
+		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the 'gym reference frame'.
 The gym reference frame is defined as a right handed coordinate system starting in the bottom left hand corner of the field where the green line meets the outer white line.
@@
 
-		\begin{align*}
-		yawAngle = currentHeading - GymOffset
-		\end{align*}
-		\begin{align*}
-		roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone 
-		\end{align*}
+		\begin{center}
+			$yawAngle = currentHeading - GymOffset$
+		\end{center}
+		\begin{center}
+			$roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone$
+		\end{center}
+
 		\[
@@
 		CR is the correction vector formulated from the corner detection vision algorithm.
-EKFdronePose is the position of the drone queried from the pixhawk.
+EKFdronePose is the position of the drone queried from the Pixhawk.
 R(3) is the rotation matrix about the third axis.
@@
 	\subsection*{Threat Avoidance}
-		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle roombas.
-This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target roombas.
+		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle Roombas.
+This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target Roombas.
 The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.
@@
 The 2000mAh 3S 15C LiPo will power the flight control board and Jetson compute units.
-		\begin{align*}
-		T(min)=Battery power(AH)*60/Total current drawn by motors
-		\end{align*}
+		\begin{center}
+			$T(min) = \frac{\text{Battery power}(AH) * 60}{\text{Total current drawn by motors}}$
+		\end{center}
+
 		Assuming an average throttle of 65\% for maneuvering, we see a 9 A current draw from each motor, and with a 10 Ah battery, that provides us with 16 minutes of flight time with minimal maneuvering and height change.
 This gives us plenty of headroom for more intense altitude and positioning changes, which will allow us to move more quickly during the competition, a valuable asset with the given time limitation.
-		\begin{align*}
-		Max continuous Amp draw (A) = Battery capacity (Ah) * Discharge rate (C)
-		\end{align*}
+		\begin{center}
+			Max continuous Amp draw ($A$) = Battery capacity ($Ah$) $*$ Discharge rate ($C$)
+		\end{center}
+
 		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 A and maximum practical current draw of 19.4 A required by the motors.
@@
 		\subsubsection*{Checklist}
-			\begin{enumerate}
+			\begin{my_enumerate}
 				\item Check battery voltage (12.0-12.6v) and insert
@@
 				\item Mode switch to Autonomous
-			\end{enumerate}
+			\end{my_enumerate}
 	\subsection*{Man/Machine Interface}
@@
 		\subsubsection*{Shock/Vibration Isolation}
-		The modern pixhawk flight controller contains internal damping from the vibration of the drone’s structure.
+		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure.
 The decided there is no need for extra damping.
 After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts.
-The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognise landing.
+The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognize landing.
 Because of this, nominal landings will not interfere with the guidance or navigation of the drone.
@@
 \section*{Conclusion}
-		Texas Aerial Robotics’ solution to the challenges provided by IARC mission 7 are bountiful and diverse.
+		Texas Aerial Robotics' solution to the challenges provided by IARC Mission 7 are bountiful and diverse.
 The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success, Unique software utilizes input from an expansive battery of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area.
@@
 	\nocite{redmon2016yolo9000}
+	\nocite{GitHubSPACEROBOTICS}
+	\nocite{HoughTransform}
+	\nocite{CannyEdgeDetection}
 	\bibliography{bibliography}

### 2018-06-01 IARC_Paper_2018/Paper.tex
Marks changes

@@
 		\subsection*{Target Identification}
-			For target identification, the drone carries five Logitech C270 USB webcams.
+			For target identification, the drone carries four Logitech C270 USB webcams and one Logitech C210 USB webcam.
 One of the cameras is located at the bottom of the drone and faces straight downward.
@@
 
-				Pixel given from YOLO: $PIX$ Pixel number of the center:
+				Pixel given from YOLO: $PIX$
 
 				\begin{center}
-					$PIX = \frac{PIX\_MAX}{2}$
+					Pixel number of the center: $PIX\_CTR = \frac{PIX\_MAX}{2}$
 				\end{center}
 
-				Define $\phi$ as portion of angle from center image to pixel detected:
+				Define $\psi$ as portion of angle from center image to pixel detected:
 
 				\begin{center}
-					$\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
+					$\psi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
 				\end{center}
@@
 
-						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:
+						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$, Then:
 						\begin{center}
-							$REAL = z * tan(\theta + \frac{\phi}{2})$
+							$REAL = z * tan(\theta + \frac{\psi}{2})$
 						\end{center}
-						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:
+						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$, Then:
 						\begin{center}
-							$REAL = z * tan(\theta - \frac{\phi}{2})$
+							$REAL = z * tan(\theta - \frac{\psi}{2})$
 						\end{center}
 				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
-						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$
+						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$
 						\begin{center}
-							$REAL = z * tan(\theta - \frac{\phi}{2})$
+							$REAL = z * tan(\theta - \frac{\psi}{2})$
 						\end{center}
-						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$
+						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$
 						\begin{center}
-							$REAL = z * tan(\theta + \frac{\phi}{2})$
+							$REAL = z * tan(\theta + \frac{\psi}{2})$
 						\end{center}
@@
 		\end{center}
+
+		This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
 

### 2018-06-01 IARC_Paper_2018/Paper.tex
Small spelling standarizations

@@
 		\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
-		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
+		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
 		\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
@@
 		\path [line, dashed] (Jetson) -- (Pixhawk);
-		\path [line, dashed] (LIDAR) -- (Pixhawk);
+		\path [line, dashed] (LiDAR) -- (Pixhawk);
 		\path [line, dashed] (Pixhawk) -- (Telemetry);
@@
 			Our system builds off of the robust open source project Arducopter.
-Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LIDAR and the optical flow sensor.
+Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR and the optical flow sensor.
 The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
@@
 This has been done to allow our drone to navigate in GPS denied environments.
-For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LIDAR and the optical flow sensor.
+For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR and the optical flow sensor.
 The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions.
@@
 		% 			\node [block, below right of=EKF] (Strategy) {Strategy};
-		% 			\node [block, below right of=Strategy] (2DLIDAR) {2D LIDAR};
+		% 			\node [block, below right of=Strategy] (2DLiDAR) {2D LiDAR};
 		% 			\node [block, right of=Strategy] (mavros) {mavros};
@@
 		% 			\path [line] (Vision) -- (Strategy);
-		% 			\path [line] (2DLIDAR) -- (Strategy);
-		% 			\path [line] (2DLIDAR) -- (mavros);
+		% 			\path [line] (2DLiDAR) -- (Strategy);
+		% 			\path [line] (2DLiDAR) -- (mavros);
 		% 			\path [line] (Strategy) -- (mavros);
@@
 		\subsubsection*{Flight Termination System}
-			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch.
+			Our drone houses a 40 [A] brushless ESC connected to a RC receiver, which acts as our kill switch.
 In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.
@@
 \section*{Payload}
-	The Drone has been designed to carry all the necessary GNC sensors, 2d LIDAR, and array of cameras and 3 nvidia TX2 Jetsons.
-In addition the drone carries a telemetry radio, kill switch and rc receiver in order to carry out safe flight.
+	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and array of cameras and 3 Nvidia Jetson TX2s.
+In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
 	\subsection*{Sensor Suite}
@@
 			The quadcopter uses eight sensors for flight control.
-The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
+The main sensors used for the navigation of the quadcopter are a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
 
@@
 				\item Check battery voltage (12.0-12.6v) and insert
-				\item Make sure LIDAR and PX4FLOW are not covered
+				\item Make sure LiDAR and PX4FLOW are not covered
 				\item Make sure that ESCs are plugged in to the right pins

### 2018-06-01 IARC_Paper_2018/Paper.tex
More standarization
Formatting changes

@@
 
-	\subsection{Yearly Milestones}
+	\subsection*{Yearly Milestones}
 	2017 - Have a working bot, with computer vision software in working or nearly working
@@
 
-			The 1-D LiDAR module used is the LiDAR-lite v3 from Garmin.
+			The 1D LiDAR module used is the LiDAR-lite v3 from Garmin.
 This one dimensional sensor is directed downwards and provides data that is used to determine altitude.
@@
 		\begin{center}
-			$T(min) = \frac{\text{Battery power}(AH) * 60}{\text{Total current drawn by motors}}$
+			$T_{min} = \frac{\text{Battery power}(AH) * 60}{\text{Total current drawn by motors}}$
 		\end{center}
@@
 
-		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 A and maximum practical current draw of 19.4 A required by the motors.
-The 10000 mAh battery with a 10C discharge rate gives us a maximum continuous current draw of 100 A, matching the limit of the motors.
+		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 [A] and maximum practical current draw of 19.4 [A] required by the motors.
+The 10000 [mAh] battery with a 10C discharge rate gives us a maximum continuous current draw of 100 [A], matching the limit of the motors.
 
-		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above-10 minute flight times at speeds below 15 mph
+		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above-10 minute flight times at speeds below 15 [mph]
 
-		INSERT GRAPH
+		\begin{figure}[!htbp]
+			\begin{center}
+				\includegraphics[width=0.75\textwidth]{powerGraph}
+			\end{center}
+		\end{figure}
 
-		As for the 2000 mAh 3S battery, this battery powers our Pixhawk flight controller and our three Jetson TX2 compute units.
+		As for the 2000 [mAh] 3S battery, this battery powers our Pixhawk flight controller and our three Jetson TX2 compute units.
 This was done partly to dedicate the entirety of the main battery to propulsion to maximize flight time.
 The other reason is that the speed controllers we chose (T-motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution.
-2000 mAh was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.
+2000 [mAh] was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.
 

### 2018-06-01 IARC_Paper_2018/Paper.tex
Changes

@@
 
-				\begin{center}
 				Pixel number of the center: $PIX\_CTR = \frac{PIX\_MAX}{2}$
-				\end{center}
 
@@
 						\begin{center}
-							$REAL = z * tan(\theta - \frac{\psi}{2})$
+							$REAL = z * tan(\theta - \frac{\psi}{2})$6s
 						\end{center}
@@
 						\end{center}
-				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
+				This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $PIX\_MAX$ and bottom is $1$.
 			\end{spacing}

### 2018-06-01 IARC_Paper_2018/Paper.tex
More changes
YEET

@@
 	\subsection*{Threat Avoidance}
-		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle Roombas.
-This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target Roombas.
+		Our avoidance system takes data from a 2D LiDAR that is used to identify the obstacle Roombas.
+This data is passed and the Strategy node uses this data to weigh possible movements negatively based on their relative position to the target Roombas.
 The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.
@@
 	\subsection*{Communications}
-		On the Jetsons data is passed between software nodes via ROS.
+		On the Jetsons, data is passed between software nodes via ROS.
 Data in between our multiple Jetsons is passed via ros messages through direct ethernet connections.
-Commands to flight commuter are passed via serial connection with data encoded in MAVLINK messages.
+Commands to the flight computer are passed via serial connection with data encoded in MAVLINK messages.
 

### 2018-06-01 IARC_Paper_2018/Paper.tex
Slight changes

@@
 The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions.
-In addition, the strategy node takes in data from computer vision and 2d lidar.
+In addition, the strategy node takes in data from computer vision and 2D LiDAR.
 The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination.
@@
 These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
-			The 2D LiDAR sensor is the SWEEP sensor by Scanse.This is a single lidar that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection.
+			The 2D LiDAR sensor is the SWEEP sensor by Scanse.
+This is a single LiDAR that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection.
 We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.
@@
 						\begin{center}
-							$REAL = z * tan(\theta - \frac{\psi}{2})$6s
+							$REAL = z * tan(\theta - \frac{\psi}{2})$
 						\end{center}
 				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
+
 						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$
@@
 		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure.
-The decided there is no need for extra damping.
+The team decided there is no need for extra damping.
 After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts.

### 2018-06-01 IARC_Paper_2018/Paper.tex
too many lines or something
Graph changes

@@
 		% Place nodes
-		\node [block] (battery) {Battery};
-		\node [block, below of=battery] (siphon) {Power siphon};
+		\node [block] (electronicsBattery) {Electonics Battery};
+		\node [block, right of=electronicsBattery, xshift=2.5cm] (motorBattery) {Motor Battery};
+		\node [block, below of=electronicsBattery] (siphon) {Power siphon};
 		\node [block, below of=siphon] (Pixhawk) {Pixhawk};
-		\node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
-		\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
+		\node [block, below right of=electronicsBattery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
+		\node [block, below left of=electronicsBattery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
 		\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
 		\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
-		\node [block, below right of=Jetson] (Camera) {Cameras};
-		\node [block, below left of=Jetson] (2dLidar) {2D LiDAR};
+		\node [block, below right of=Jetson, yshift=-.5cm] (Camera) {Cameras};
+		\node [block, below left of=Jetson, yshift=-.5cm] (2dLidar) {2D LiDAR};
 		\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
@@
 		% Draw edges
-		\path [line] (battery) -- (siphon);
+		\path [line] (electronicsBattery) -- (siphon);
 		\path [line] (siphon) -- (Pixhawk);
-		\path [line] (battery) -- (PDB);
+		\path [line] (motorBattery) -- (PDB);
 		\path [line] (PDB) -- (ESCs);
-		\path [line] (battery) -- (Jetson);
+		\path [line] (electronicsBattery) -- (Jetson);
 		\path [line, dashed] (Camera) -- (Jetson);
@@
 	\end{tikzpicture}
-	\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
+	\caption*{Flowchart of quadcopter electronics \\ \scriptsize *Solid arrows indicate power while dashed lines indicate power+data}
 	\end{center}
@@
 
-		This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
-
 		\[

### 2018-06-01 IARC_Paper_2018/Paper.tex
Finishing touches on bibliography

@@
 \usepackage{setspace}
+\usepackage{hyperref}
 
@@
 %%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
-\affiliatedauthor{Noel Brownback}{The University of Texas at Austin}
-\affiliatedauthor{Anthony Carreon}{The University of Texas at Austin}
-\affiliatedauthor{Shayer Hassan}{The University of Texas at Austin}
-\affiliatedauthor{Eric Johnson}{The University of Texas at Austin}
-\affiliatedauthor{Colin Lewis}{The University of Texas at Austin}
-\affiliatedauthor{Mark Loveland}{The University of Texas at Austin}
-\affiliatedauthor{Umer Salman}{The University of Texas at Austin}
+\affiliatedauthor{Noel Brownback}{\vspace{-.5cm}}
+\affiliatedauthor{Anthony Carreon}{\vspace{-.5cm}}
+\affiliatedauthor{Shayer Hassan}{\vspace{-.5cm}}
+\affiliatedauthor{Eric Johnson}{\vspace{-.5cm}}
+\affiliatedauthor{Colin Lewis}{\vspace{-.5cm}}
+\affiliatedauthor{Mark Loveland}{\vspace{-.5cm}}
+\affiliatedauthor{Umer Salman}{\vspace{-.5cm}}
 \affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
@@
 	\subsection*{Yearly Milestones}
+
 	2017 - Have a working bot, with computer vision software in working or nearly working
+
 	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability
@@
 \section*{Payload}
-	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and array of cameras and 3 Nvidia Jetson TX2s.
+	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and an array of cameras and 3 Nvidia Jetson TX2s.
 In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
@@
 			The quadcopter uses eight sensors for flight control.
-The main sensors used for the navigation of the quadcopter are a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
+The main sensors used for the navigation of the quadcopter are: a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our Pixhawk 2 flight control board.
 
@@
 			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles.
-The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
+The quadcopter is equipped with a single downward facing camera and four outward facing cameras for image recognition, as well as a two-dimensional plane LiDAR sensor for obstacle avoidance.
+
 			The singular bottom camera is a Logitech C210 webcam.
@@
 
+			\pagebreak
 				\textbf{Transformation}:

### 2018-06-01 IARC_Paper_2018/Paper.tex
Well there were a lot of typos and stuff still...

@@
 	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7.
-A combination of lightweight materials and powerful propulsion enables optimizes flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand.
+A combination of lightweight materials and powerful propulsion optimizes flight time, while standardized flight control systems supported by a massive community enables customization and adaptation to the mission at hand.
 This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft.
@@
 Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone.
-Thus, Mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden.
+Thus, Mission 7 requires novel solutions to deriving this critical telemetry, as GPS is forbidden.
 Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.
@@
 	Texas Aerial Robotics addresses these challenges by utilizing computer vision.
-Through computer vision the drone has the ability to both understand its location, and also track targets in real time.
+Through computer vision, the drone has the ability to both understand its location and also track targets in real time.
 The drone records the data and position of the objects, simulating those which lie beyond the field of view, which allows for strategic analysis and definition based on estimates of unseen/out of sight targets.
@@
 
-	2017 - Have a working bot, with computer vision software in working or nearly working
+	2017 - Have a working bot, with computer vision software in working or nearly working state
 
@@
 	\subsection*{Propulsion and Lift System}
-			The vehicle utilizes a x-y axis symmetrical quad-rotor system.
-This provides a balanced airframe optimized for omni-directional maneuvering.
+			The vehicle utilizes an x-y axis symmetrical quad-rotor system.
+This provides a balanced airframe optimized for omnidirectional maneuvering.
 The frame is lifted by four T-Motor U3 KV700 motors.
 These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust.
-This is necessary for our 3.15 kg weight to maintain a 2.2 thrust-to-weight ratio ideal for battery life and flight time.
+This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.
 
@@
 			Our system builds off of the robust open source project Arducopter.
-Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR and the optical flow sensor.
+Arducopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR, and the optical flow sensor.
 The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
@@
 			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin.
-This has been done to allow our drone to navigate in GPS denied environments.
-For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR and the optical flow sensor.
-The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions.
+This has been done to make our drone capable of navigating in GPS denied environments.
+For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR, and the optical flow sensor.
+The EKF position is then queried via mavros so that our strategy code can use our position to make intelligent decisions.
 In addition, the strategy node takes in data from computer vision and 2D LiDAR.
-The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination.
-Over time, the EKF will have error in comparison to reality.
-To combat this, the control node will input a correction vector.
+The strategy node then determines a waypoint and mode, and the ROS controls node will do a sanity check on the waypoint and publish the waypoint until the drone has reached its destination.
+Over time, the EKF will have some error in comparison to reality.
+To combat this, the controls node will input a correction vector.
 This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid.
-This algorithm goes as follows.
-Gaussian blur, color threshold, erosion, dilation, Canny, Hough, line intersection, and non maximum suppression.
+This algorithm goes as follows: Gaussian blur, color threshold, erosion, dilation, Canny edge detection, Hough transform, line intersection, and non-maximum suppression.
 
@@
 
-		% \begin{figure}[!htbp]
-		% 	\begin{center}
-		% 		\begin{tikzpicture}[node distance = 3cm, auto]
-		% 			% Place nodes
-		% 			\node [block] (IMU) {IMU + Flow};
-		% 			\node [block, below of=IMU] (Camera) {Camera};
-		% 			\node [block, right of=IMU] (EKF) {EKF};
-		% 			\node [block, below of=EKF] (Vision) {Vision};
-		% 			\node [block, below right of=EKF] (Strategy) {Strategy};
-		% 			\node [block, below right of=Strategy] (2DLiDAR) {2D LiDAR};
-		% 			\node [block, right of=Strategy] (mavros) {mavros};
-		% 			\node [block, right of=mavros] (Pixhawk) {Pixhawk};
-		% 			\node [block, right of=Pixhawk] (Move) {Move};
-		% 			% Draw edges
-		% 			\path [line] (IMU) -- (EKF);
-		% 			\path [line] (Camera) -- (Vision);
-		% 			\path [line] (EKF) -- (Strategy);
-		% 			\path [line] (Vision) -- (Strategy);
-		% 			\path [line] (2DLiDAR) -- (Strategy);
-		% 			\path [line] (2DLiDAR) -- (mavros);
-		% 			\path [line] (Strategy) -- (mavros);
-		% 			\path [line] (mavros) -- (Pixhawk);
-		% 			\path [line] (Pixhawk) -- (Move);
-		% 		\end{tikzpicture}
-		% 		\caption*{Overview of control system}
-		% 	\end{center}
-		% \end{figure}
-
 		\subsubsection*{Flight Termination System}
-			Our drone houses a 40 [A] brushless ESC connected to a RC receiver, which acts as our kill switch.
-In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.
+			Our drone houses a 40 [A] brushless ESC connected to an RC receiver, which acts as our kill switch.
+In the event of catastrophic failure, the safety operator can send the kill signal, and all power will be cut from the drone's systems.
 
 \section*{Payload}
-	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and an array of cameras and 3 Nvidia Jetson TX2s.
-In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
+	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s.
+In addition, the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
 	\subsection*{Sensor Suite}
@@
 			The quadcopter uses eight sensors for flight control.
-The main sensors used for the navigation of the quadcopter are: a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our Pixhawk 2 flight control board.
+The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.
 
-			The 1D LiDAR module used is the LiDAR-lite v3 from Garmin.
-This one dimensional sensor is directed downwards and provides data that is used to determine altitude.
-The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring distance travelled and direction.
+			The 1D LiDAR module used is the LIDAR-Lite v3 from Garmin.
+This one-dimensional sensor is directed downward and provides data that is used to determine altitude.
+The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction.
 The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses.
-The data from these sensors is used by the Pixhawk onboard system for flight control and the maneuvering of the quadcopter.
+The data from these sensors is used by the Pixhawk onboard system for flight control and maneuvering of the quadcopter.
 
 		\subsubsection*{Mission Sensors}
-			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles.
+			For completion of Mission 7, the drone must be able to detect Roombas and obstacles.
 The quadcopter is equipped with a single downward facing camera and four outward facing cameras for image recognition, as well as a two-dimensional plane LiDAR sensor for obstacle avoidance.
@@
 			The singular bottom camera is a Logitech C210 webcam.
-This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270.
+This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.
+The four peripheral cameras are Logitech 960 C270s.
 These are used to recognize and track the Roombas around the playing field.
-These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
+These five webcams provide enough information to allow the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
 			The 2D LiDAR sensor is the SWEEP sensor by Scanse.
@@
 			In order to accomplish the first objective, an open source software package developed by Joseph Redmon called YOLO (You Only Look Once) is used.
-More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher frame rates.
+More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher framerates.
 YOLO is a neural network that can identify user-defined objects once it has been trained.
@@
 			After YOLO outputs the pixel locations of each identified target Roomba, the final objective is to transform these pixel coordinates into x-y coordinates relative to the drone.
-In addition to the pixel coordinate (PIX \#), the other knowns are height ($z$), camera rotation angle relative to downward facing ($\theta$), and field of view ($\phi$), as well as total pixels in x and y (PIX\_MAX).
+In addition to the pixel coordinate ($PIX \#$), the other knowns are height ($z$), camera rotation angle relative to downward facing ($\theta$), and field of view ($\phi$), as well as total pixels in $x$ and $y$ ($PIX\_MAX$).
 Here is a diagram to illustrate these knowns below:
@@
 						\end{center}
-				This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $PIX\_MAX$ and bottom is $1$.
+				This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ `top' of frame is $PIX\_MAX$ and bottom is $1$.
 			\end{spacing}
 
-		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the 'gym reference frame'.
-The gym reference frame is defined as a right handed coordinate system starting in the bottom left hand corner of the field where the green line meets the outer white line.
-This transformation is defined as followed.
+		Once the coordinate X, Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the `gym reference frame.' The gym reference frame is defined as a right-handed coordinate system starting in the bottom left-hand corner of the field where the green line meets the outer white line.
+This transformation is defined as follows:
 
@@
 R(3) is the rotation matrix about the third axis.
-GymOffset is the direction of the 2 axis defined during the startup sequence before flight.
+GymOffset is the direction of the 2 axes defined during the startup sequence before flight.
 The new coordinate in the gym frame is passed off to the strategy node as data to be acted on.
@@
 		Our avoidance system takes data from a 2D LiDAR that is used to identify the obstacle Roombas.
-This data is passed and the Strategy node uses this data to weigh possible movements negatively based on their relative position to the target Roombas.
-The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.
+This data is passed and the strategy node uses this data to weigh possible movements negatively based on their relative position to the obstacle Roombas.
+The controls node also will use the data, such as in the event an obstacle robot is within 1.5 [m], in which case controls node will issue a waypoint opposite of the minimum vector.
 
@@
 		On the Jetsons, data is passed between software nodes via ROS.
-Data in between our multiple Jetsons is passed via ros messages through direct ethernet connections.
+Data in between our multiple Jetsons is passed via ROS messages through direct ethernet connections.
 Commands to the flight computer are passed via serial connection with data encoded in MAVLINK messages.
@@
 	\subsection*{Power Management System}
-		The quadcopter uses a 10000mAh 4S 10C LiPo battery and a 2000mAh 3S 15C LiPo battery for power.
-The 10000mAh 4S 10C LiPo is used to power our ESCs and Motors.
-With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 grams of thrust per motor needed for hovering flight.
-The 2000mAh 3S 15C LiPo will power the flight control board and Jetson compute units.
+		The quadcopter uses a 10000 [mAh] 4S 10C LiPo battery and a 2000 [mAh] 3S 15C LiPo battery for power.
+The 10000 [mAh] 4S 10C LiPo is used to power our ESCs and Motors.
+With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 [grams] of thrust per motor needed for hovering flight.
+The 2000 [mAh] 3S 15C LiPo will power the flight control board and Jetson compute units.
 		\begin{center}
@@
 
-		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above-10 minute flight times at speeds below 15 [mph]
+		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph]
 
@@
 		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure.
-The team decided there is no need for extra damping.
+The team decided that there is no need for extra damping.
 After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts.
-The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognize landing.
+The team believes there is no need to have landing shocks, as the sophisticated Arducopter flight stack has logic to recognize landing.
 Because of this, nominal landings will not interfere with the guidance or navigation of the drone.
@@
 Our prop guards took multiple iterations.
-We wanted a design that would not interfere with the prop wash, but still be able prevent damage to the quadcopter itself in the unfortunate event of collision.
+We wanted a design that would not interfere with the prop wash, but still be able to prevent damage to the quadcopter itself in the unfortunate event of a collision.
 The first iteration looked nice, but interfered with the prop wash too much and weighed too much, reducing the thrust.
@@
 		To safely test our software throughout the development process, the team implemented a simulation using the Gazebo application.
-Using this tool, TAR was able to deploy full scale software in the loop simulation without jeopardizing hardware with each design iteration.
+Using this tool, TAR was able to deploy full-scale software in the loop simulation without jeopardizing hardware with each design iteration.
 
-		To employ the Gazebo framework, the team imported a standard quadcopter model from the arducopter standard library and roomba models from Gazebo model library, which were then updated with the color coded plates and obstacle tubes prescribed for the competition.
-Additionally, the ground plain within the reproduction was changed to match the texture expected at the competition.
+		To employ the Gazebo framework, the team imported a standard quadcopter model from the ArduCopter standard library and Roomba models from Gazebo model library, which were then updated with the color-coded plates and obstacle tubes prescribed for the competition.
+Additionally, the ground plane within the reproduction was changed to match the texture expected at the competition.
 
@@
 With this congruence, the exact same software run onboard the drone could be run within the simulation, complete with sensor feedback detected within the simulated instance.
-C++ scripts could then be utilized to enforce the correct roomba behaviors, scripting the robots using the same messaging environment as the quadcopter itself (ROS).
+C++ scripts could then be utilized to enforce the correct Roomba behaviors, scripting the robots using the same messaging environment as the quadcopter itself (ROS).
 
 		Overall, modeling our software behavior within a Gazebo simulation greatly expedited the development process.
-By standardizing the simulation setup, tests could be conducted on multiple computers at any time, instead of requiring sluggish process of updating, calibrating, and flying the physical drone.
+By standardizing the simulation setup, tests could be conducted on multiple computers at any time, instead of requiring the sluggish process of updating, calibrating, and flying the physical drone.
 Additionally, simulation protected the hardware from the accidents and unintentional flight behavior inherent to prototype software.
@@
 Eventually, refined software was tested on a model testbed or on the drone itself.
-Much of the computer vision and general software integration was developed on this testbed, where performance could be verified with the same sensors and computational hardware as the aircraft before full scale deployment.
+Much of the computer vision and general software integration was developed on this testbed, where performance could be verified with the same sensors and computational hardware as the aircraft before full-scale deployment.
 Even strategy nodes could be tested on this platform, with waypoint predictions vetted before being deployed to the aircraft.
@@
 		Flight tests, expectedly, require a specific setting.
-Generally, Texas Aerial Robotics tested on the roof of the Aerospace building on campus at the The University of Texas.
+Generally, Texas Aerial Robotics tested on the roof of the Aerospace building on campus at The University of Texas at Austin.
 This controlled environment bore witness to hardware implementation throughout our design process, from original flight readiness to early autonomy.
@@
 
-		Regardless of the setting, each flight test was conducted with constant apparatus.
-A four meter by four meter test mat printed with the pattern expected at competition, to allow optical flow for navigation.
-Across this mat drives a test roomba, which accurately recreates both the physical appearance and behaviors of those robots that will be tracked at the venue, complete with top plate and switch.
+		Regardless of the setting, each flight test was conducted with constant apparatus: a four meter by four meter test mat printed with the pattern expected at competition to allow optical flow for navigation.
+Across this mat drives a test Roomba, which accurately recreates both the physical appearance and behaviors of those robots that will be tracked at the venue, complete with top plate and switch.
 Finally, there is the drone itself, which starts on a corner of the mat, takes off autonomously, and then executes the maneuver to be tested.
@@
 \section*{Conclusion}
-		Texas Aerial Robotics' solution to the challenges provided by IARC Mission 7 are bountiful and diverse.
-The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success, Unique software utilizes input from an expansive battery of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area.
+	Texas Aerial Robotics' solutions to the challenges provided by IARC Mission 7 are bountiful and diverse.
+The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success.
+Unique software utilizes input from an expansive collection of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area.
 Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.

### 2018-06-01 IARC_Paper_2018/Paper.tex
Uh we had some things not best in formatting

@@
 
-\section*{Introduction}
+\section*{INTRODUCTION}
 	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone.
@@
 
+	\pagebreak
 	\subsection*{Yearly Milestones}
@@
 
-\section*{Air Vehicle}
+\section*{AIR VEHICLE}
 	\subsection*{Propulsion and Lift System}
@@
 
-\section*{Payload}
+\section*{PAYLOAD}
 	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s.
@@
 
-		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph]
+		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph].
 
@@
 
-\section*{Operations}
+\section*{OPERATIONS}
 	\subsection*{Flight Preparations}
@@
 			\begin{my_enumerate}
-				\item Check battery voltage (12.0-12.6v) and insert
+				\item Check battery voltage (12.0-12.6V) and insert
 				\item Make sure LiDAR and PX4FLOW are not covered
@@
 
-\section*{Risk Reduction}
+\section*{RISK REDUCTION}
 	\subsection*{Vehicle Status}
@@
 
-\section*{Conclusion}
+\section*{CONCLUSION}
 	Texas Aerial Robotics' solutions to the challenges provided by IARC Mission 7 are bountiful and diverse.

### 2018-06-01 IARC_Paper_2018/Paper.tex
Ignore this commit. Look at the 2 commits before this one.

@@
 This was done partly to dedicate the entirety of the main battery to propulsion to maximize flight time.
-The other reason is that the speed controllers we chose (T-motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution.
+The other reason is that the speed controllers we chose (T-Motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution.
 2000 [mAh] was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.

### 2019-05-31 IARC_Paper_2019/Paper.tex
Start putting 2019 in LaTeX. Also, actually write the dang thing.

--- 2018-06-01 IARC_Paper_2018/Paper.tex
@@
 %%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
-\affiliatedauthor{Noel Brownback}{\vspace{-.5cm}}
-\affiliatedauthor{Anthony Carreon}{\vspace{-.5cm}}
-\affiliatedauthor{Shayer Hassan}{\vspace{-.5cm}}
-\affiliatedauthor{Eric Johnson}{\vspace{-.5cm}}
-\affiliatedauthor{Colin Lewis}{\vspace{-.5cm}}
-\affiliatedauthor{Mark Loveland}{\vspace{-.5cm}}
-\affiliatedauthor{Umer Salman}{\vspace{-.5cm}}
-\affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
+\affiliatedauthor{Umer Salman, Mario Gonzalez}{The University of Texas at Austin}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7.
+	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 8.
 A combination of lightweight materials and powerful propulsion optimizes flight time, while standardized flight control systems supported by a massive community enables customization and adaptation to the mission at hand.
-This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft.
+This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the aiding of people to analyze and interact with an environment.
+This is done through homebrewed QR code decoding algorithms and the shared computing power onboard the multiple aircrafts.
 Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
@@
 Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone.
-Thus, Mission 7 requires novel solutions to deriving this critical telemetry, as GPS is forbidden.
-Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.
+Thus, Mission 8 requires novel solutions to deriving this critical telemetry as GPS is forbidden.
+Additionally, the aircrafts must be capable of taking commands in a humanized "natural" fashion and avoid other aircrafts without being informed of those other aircrafts' locations.
 
 	Texas Aerial Robotics addresses these challenges by utilizing computer vision.
-Through computer vision, the drone has the ability to both understand its location and also track targets in real time.
-The drone records the data and position of the objects, simulating those which lie beyond the field of view, which allows for strategic analysis and definition based on estimates of unseen/out of sight targets.
-Interaction with these objectives is achieved using the carbon fiber bottom plate of the aircraft and perimeter prop guards, a material choice that lends itself to lightweight resiliency.
+TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena while in flight and use that data in real time.
+The drone creates pointclouds of the objects in view using the stereo camera and combines sections together.
+This means that should a section of the map start showing drift, the ORBSLAM2/ORBSLAMM System will toss out just the section while maintaining as much of the map as possible.
+TAR hopes to combine the processing between the multiple drones to have them work together on one map.
+These drones also solve for the QR code that is the combination the human needs for collecting the objects.
+The drone is also built with safety for a plethora of other objects, containing man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.
 
@@
 			\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
-				% Place nodes
-				\node [block] (electronicsBattery) {Electonics Battery};
-				\node [block, right of=electronicsBattery, xshift=2.5cm] (motorBattery) {Motor Battery};
-				\node [block, below of=electronicsBattery] (siphon) {Power siphon};
+				\node [block] (battery) {Battery};
+				\node [block, below of=battery] (siphon) {Power siphon};
 				\node [block, below of=siphon] (Pixhawk) {Pixhawk};
-				\node [block, below right of=electronicsBattery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
-				\node [block, below left of=electronicsBattery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
+				\node [block, below right of=battery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
+				\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2};
 				\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
 				\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
-				\node [block, below right of=Jetson, yshift=-.5cm] (Camera) {Cameras};
-				\node [block, below left of=Jetson, yshift=-.5cm] (2dLidar) {2D LiDAR};
+				\node [block, below right of=Jetson, yshift=-.5cm] (StereoCamera) {ORBSLAM stereo camera};
+				\node [block, below of=Jetson, yshift=-.5cm] (DownCamera) {Downward camera};
+				\node [block, below left of=Jetson, yshift=-.5cm] (Sonars) {4 sonar distance sensors};
 				\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
 				\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
-				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
+				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {Downward rangefinder (ToF)};
 				\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
 				% Draw edges
-				\path [line] (electronicsBattery) -- (siphon);
+				\path [line] (battery) -- (siphon);
 				\path [line] (siphon) -- (Pixhawk);
-				\path [line] (motorBattery) -- (PDB);
+				\path [line] (battery) -- (PDB);
 				\path [line] (PDB) -- (ESCs);
-				\path [line] (electronicsBattery) -- (Jetson);
-				\path [line, dashed] (Camera) -- (Jetson);
-				\path [line, dashed] (2dLidar) -- (Jetson);
+				\path [line] (battery) -- (Jetson);
+				\path [line, dashed] (StereoCamera) -- (Jetson);
+				\path [line, dashed] (DownCamera) -- (Jetson);
+				\path [line, dashed] (Sonars) -- (Jetson);
 				\path [line, dashed] (Flow) -- (Pixhawk);
@@
 
-	2017 - Have a working bot, with computer vision software in working or nearly working state
+	2019 - Have a working system, with localization of multiple drones working together to solve the QR code and communicate with the person through voice commands in working or nearly working state.
 
-	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability
+	2020 - Finish all aspects of mission through more networking between the quadcopters, tweak the physique of the drone for better flight control and stability, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible,
 
@@
 	\subsection*{Propulsion and Lift System}
-			The vehicle utilizes an x-y axis symmetrical quad-rotor system.
-This provides a balanced airframe optimized for omnidirectional maneuvering.
-The frame is lifted by four T-Motor U3 KV700 motors.
-These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust.
+			The vehicle utilizes an y axis symmetrical quad-rotor system.
+This H-frame provides a stable quadcopter for a smaller overall package while maintaining plenty of room for electronics.
+The frame is lifted by four T-Motor MN2212 KV920-V2.0 motors.
+These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 7.2 [kg] of thrust.
 This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.
 
-			The propellers used with the motors are 13 [in] long and made of carbon fiber.
+			The propellers used with the motors are 9.5 [in] long and made of plastic.
 These T-Motor propellers provide excellent precision, durability, and efficiency.
@@
 		\subsubsection*{Stability Augmentation System}
-			Our system builds off of the robust open source project Arducopter.
-Arducopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR, and the optical flow sensor.
-The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
+			Our system builds off of the robust open source project ArduCopter.
+ArduCopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude ToF, and the optical flow sensor.
+The ArduCopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
 The vast community of developers and users ensures refined controls code with lots of features.
@@
 		\subsubsection*{Navigation}
-			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin.
+			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin.
 This has been done to make our drone capable of navigating in GPS denied environments.
-For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR, and the optical flow sensor.
-The EKF position is then queried via mavros so that our strategy code can use our position to make intelligent decisions.
-In addition, the strategy node takes in data from computer vision and 2D LiDAR.
-The strategy node then determines a waypoint and mode, and the ROS controls node will do a sanity check on the waypoint and publish the waypoint until the drone has reached its destination.
+For general waypoint navigation, the drone utilizes the ArduCopter EKF that takes in data from the IMU, compass, altitude ToF, and the optical flow sensor.
+The EKF position is then queried via mavros so that our controls code can use our position to make intelligent decisions.
+In addition, the controls node takes in data from computer vision and the sonar sensors.
+The controls node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint until the drone has reached its destination.
 Over time, the EKF will have some error in comparison to reality.
-To combat this, the controls node will input a correction vector.
-This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid.
-This algorithm goes as follows: Gaussian blur, color threshold, erosion, dilation, Canny edge detection, Hough transform, line intersection, and non-maximum suppression.
+However, using ORBSLAMM, an open-source version of ORBSLAM that contains multimapping, we are able to combat this by correcting the maps through physical objects (which will not be moving), which is then used to correct the EKF.
 
@@
 		\subsubsection*{Flight Termination System}
-			Our drone houses a 40 [A] brushless ESC connected to an RC receiver, which acts as our kill switch.
-In the event of catastrophic failure, the safety operator can send the kill signal, and all power will be cut from the drone's systems.
+			We will be using ArduCopter's EmergencyStop to act as our killswitch.
+In the event of catastrophic failure, the safety operator can send the kill signal, and all power will immediately be cut from the drone's ESCs, and in turn, the motors.
 
 \section*{PAYLOAD}
-	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s.
-In addition, the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
+	The drone has been designed to carry all the necessary GNC sensors, an array of sonar sensors, a stereo camera, a downward camera, and a Nvidia Jetson TX2.
+In addition, the drone carries a telemetry radio, WiFi antennas, and an RC receiver in order to carry out safe flight.
 	\subsection*{Sensor Suite}
@@
 
-			The 1D LiDAR module used is the LIDAR-Lite v3 from Garmin.
-This one-dimensional sensor is directed downward and provides data that is used to determine altitude.
+			The 1D LiDAR module used is a Time of Flight (ToF) sensor named the Teraranger One.
+This one-dimensional sensor is directed downward and provides data to determine altitude.
 The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction.
@@
 		\subsubsection*{Mission Sensors}
-			For completion of Mission 7, the drone must be able to detect Roombas and obstacles.
-The quadcopter is equipped with a single downward facing camera and four outward facing cameras for image recognition, as well as a two-dimensional plane LiDAR sensor for obstacle avoidance.
+			For completion of Mission 8, the drone must be able to detect the QR code and avoid obstacles, both moving and non-moving.
+The quadcopter is equipped with a single downward facing camera for reading the quadrant of the QR code.
+A stereo camera is used for ORBSLAMM for localization.
+There is also an array of sonar sensors for obstacle avoidance.
 
-			The singular bottom camera is a Logitech C210 webcam.
-This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.
-The four peripheral cameras are Logitech 960 C270s.
-These are used to recognize and track the Roombas around the playing field.
-These five webcams provide enough information to allow the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
-			The 2D LiDAR sensor is the SWEEP sensor by Scanse.
-This is a single LiDAR that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection.
-We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.
+			The singular bottom camera is a ELP webcam.
+This webcam is used for reading the QR code quadrant.
+The stereo camera in front is also an ELP camera.
+These cameras were chosen for their very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad.
+			The array of sonar sensors contains 4 MAXBOTICS 7m I2C sonars.
+These allow the drone to detect objects on the sides the quadcopter intends to move in.
+We chose to use this for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power.
+Sonar sensors are very tried and true.
+Additionally, we opted for sonar rather than radar as radar has a harder time picking up smaller objects, like a drone.
 
@@
 
-			\begin{figure}[!htbp]
-				\begin{center}
-					\includegraphics[width=0.75\textwidth]{roomba}
-				\end{center}
-			\end{figure}
+			%\begin{figure}[!htbp]
+			%	\begin{center}
+			%		\includegraphics[width=0.75\textwidth]{roomba}
+			%	\end{center}
+			%\end{figure}
 

### 2019-05-31 IARC_Paper_2019/Paper.tex
Work
Paper is in order, info needs to be cleaned up and fleshed out

@@
 
-\title{Intelligent Quadcopter for IARC 2018}
+\title{Intelligent Quadcopter for IARC 2019}
 
@@
 %%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
-\affiliatedauthor{Umer Salman, Mario Gonzalez}{The University of Texas at Austin}
+\affiliatedauthor{Umer Salman, Noel Brownback, Eric Johnson, Mario Gonzalez}{The University of Texas at Austin}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 8.
+	Texas Aerial Robotics has constructed a custom quadrotor aircraft system for the fulfillment of the International Aerial Robotics Competition Mission 8.
 A combination of lightweight materials and powerful propulsion optimizes flight time, while standardized flight control systems supported by a massive community enables customization and adaptation to the mission at hand.
@@
 These drones also solve for the QR code that is the combination the human needs for collecting the objects.
-The drone is also built with safety for a plethora of other objects, containing man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.
+TAR implements the "humanized" control aspect of the system through voice control using an Android app that connects to all of the air vehicles.
+The drones are also built with safety features for a plethora of other objects that may be on the field through its man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.
 
@@
 				\node [block, below right of=battery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
-				\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2};
+				\node [block, below left of=battery, xshift=-3cm, yshift=-.5cm] (Jetson) {Nvidia Jetson TX2};
 				\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
 				\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
-				\node [block, below right of=Jetson, yshift=-.5cm] (StereoCamera) {ORBSLAM stereo camera};
-				\node [block, below of=Jetson, yshift=-.5cm] (DownCamera) {Downward camera};
-				\node [block, below left of=Jetson, yshift=-.5cm] (Sonars) {4 sonar distance sensors};
-				\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
-				\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
-				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {Downward rangefinder (ToF)};
-				\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
+				\node [block, below right of=Jetson, yshift=-.5cm, align=center] (StereoCamera) {ORBSLAM \\ stereo camera};
+				\node [block, below of=Jetson, xshift=-2cm, yshift=-1.1cm, align=center] (DownCamera) {Downward camera};
+				\node [block, xshift=-2cm, yshift=-.2cm, below left of=Jetson, align=center] (Sonars) {4 sonar \\ distance sensors};
+				\node [block, below right of=Pixhawk, yshift=-1.2cm] (Flow) {PX4FLOW};
+				\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1.2cm] (Spektrum) {Spektrum controller};
+				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1.2cm, align=center] (LiDAR) {Downward \\ LiDAR};
+				\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1.2cm, align=center] (Telemetry) {Ground \\ Telemetry};
 				% Draw edges
@@
 
-	2019 - Have a working system, with localization of multiple drones working together to solve the QR code and communicate with the person through voice commands in working or nearly working state.
+	2019 - Have a working system, with localization and GPS-denied navigation of multiple drones.
+These drones should work together to solve the QR code and communicate with a person through an Android app that can transmit voice commands to the drones.
 
-	2020 - Finish all aspects of mission through more networking between the quadcopters, tweak the physique of the drone for better flight control and stability, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible,
+	2020 - Finish all aspects of mission through more networking between the quadcopters, tweak the physique of the drone for better flight control and stability, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible.
 
@@
 The frame is lifted by four T-Motor MN2212 KV920-V2.0 motors.
-These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 7.2 [kg] of thrust.
+These motors provide
+			------------fix these numbers---------- 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 7.2 [kg] of thrust.
 This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.
@@
 The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.
-
-	\subsection*{Guidance, Navigation, and Control}
-		\subsubsection*{Stability Augmentation System}
-			Our system builds off of the robust open source project ArduCopter.
-ArduCopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude ToF, and the optical flow sensor.
-The ArduCopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
-The vast community of developers and users ensures refined controls code with lots of features.
-
-		\subsubsection*{Navigation}
-			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin.
-This has been done to make our drone capable of navigating in GPS denied environments.
-For general waypoint navigation, the drone utilizes the ArduCopter EKF that takes in data from the IMU, compass, altitude ToF, and the optical flow sensor.
-The EKF position is then queried via mavros so that our controls code can use our position to make intelligent decisions.
-In addition, the controls node takes in data from computer vision and the sonar sensors.
-The controls node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint until the drone has reached its destination.
-Over time, the EKF will have some error in comparison to reality.
-However, using ORBSLAMM, an open-source version of ORBSLAM that contains multimapping, we are able to combat this by correcting the maps through physical objects (which will not be moving), which is then used to correct the EKF.
-
-		\begin{figure}[!htbp]
-			\begin{center}
-				\includegraphics[width=0.75\textwidth]{system}
-				\caption*{Overview of control system}
-			\end{center}
-		\end{figure}
-
-		\subsubsection*{Flight Termination System}
-			We will be using ArduCopter's EmergencyStop to act as our killswitch.
-In the event of catastrophic failure, the safety operator can send the kill signal, and all power will immediately be cut from the drone's ESCs, and in turn, the motors.
-
-\section*{PAYLOAD}
-	The drone has been designed to carry all the necessary GNC sensors, an array of sonar sensors, a stereo camera, a downward camera, and a Nvidia Jetson TX2.
-In addition, the drone carries a telemetry radio, WiFi antennas, and an RC receiver in order to carry out safe flight.
-	\subsection*{Sensor Suite}
-		\subsubsection*{GNC Sensors}
-			The quadcopter uses eight sensors for flight control.
-The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.
-
-			The 1D LiDAR module used is a Time of Flight (ToF) sensor named the Teraranger One.
-This one-dimensional sensor is directed downward and provides data to determine altitude.
-The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction.
-The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses.
-The data from these sensors is used by the Pixhawk onboard system for flight control and maneuvering of the quadcopter.
-
-		\subsubsection*{Mission Sensors}
-			For completion of Mission 8, the drone must be able to detect the QR code and avoid obstacles, both moving and non-moving.
-The quadcopter is equipped with a single downward facing camera for reading the quadrant of the QR code.
-A stereo camera is used for ORBSLAMM for localization.
-There is also an array of sonar sensors for obstacle avoidance.
-
-			The singular bottom camera is a ELP webcam.
-This webcam is used for reading the QR code quadrant.
-The stereo camera in front is also an ELP camera.
-These cameras were chosen for their very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad.
-			The array of sonar sensors contains 4 MAXBOTICS 7m I2C sonars.
-These allow the drone to detect objects on the sides the quadcopter intends to move in.
-We chose to use this for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power.
-Sonar sensors are very tried and true.
-Additionally, we opted for sonar rather than radar as radar has a harder time picking up smaller objects, like a drone.
-
-		\subsection*{Target Identification}
-			For target identification, the drone carries four Logitech C270 USB webcams and one Logitech C210 USB webcam.
-One of the cameras is located at the bottom of the drone and faces straight downward.
-The other four cameras are mounted on the bottom side of each arm facing outward.
-All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.
-
-			There are two main objectives that need to be completed to successfully relay target information to the strategy node.
-The first objective is to take in the raw video data and detect the target Roombas so that pixel numbers of the centroids of the Roombas in the frame can be sent as output.
-The second objective is to take the pixel numbers of the centroids of the detected Roombas as input, and then output x and y coordinates relative to the drone using a coordinate transformation and the known height and orientation of the camera with respect to the floor.
-
-			In order to accomplish the first objective, an open source software package developed by Joseph Redmon called YOLO (You Only Look Once) is used.
-More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher framerates.
-YOLO is a neural network that can identify user-defined objects once it has been trained.
-After training the neural network by feeding in approximate 2000 photos of the target Roombas (with the Roombas identified manually), YOLO can reliably identify target Roombas in real time.
-An example is displayed below:
-
-			%\begin{figure}[!htbp]
-			%	\begin{center}
-			%		\includegraphics[width=0.75\textwidth]{roomba}
-			%	\end{center}
-			%\end{figure}
-
-			After YOLO outputs the pixel locations of each identified target Roomba, the final objective is to transform these pixel coordinates into x-y coordinates relative to the drone.
-In addition to the pixel coordinate ($PIX \#$), the other knowns are height ($z$), camera rotation angle relative to downward facing ($\theta$), and field of view ($\phi$), as well as total pixels in $x$ and $y$ ($PIX\_MAX$).
-Here is a diagram to illustrate these knowns below:
-
-			\begin{tikzpicture}[scale=3]
-				\coordinate [label=left:$X$] (X) at (-1.5cm,-1cm);
-				\coordinate [label=right:$Y$] (Y) at (1.5cm,-1cm);
-				\coordinate [label=above:$Z$] (Z) at (-1.5cm,1cm);
-				\coordinate (phi) at (.1cm,-1cm);
-				\coordinate (theta) at (-.75cm,-1cm);
-				\draw[<->] (Z) -- node[below] {} (X) -- node[right] {} (Y);
-				\draw[dashed](Y) -- node[above left] {} (Z);
-				\draw[dashed] (Z) -- node[below] {} (phi);
-				\draw[dashed] (Z) -- node[below] {} (theta);
-				\tkzMarkRightAngle[draw=black](Z,X,Y)
-				\tkzDrawPoints[color=black,fill=white](X)
-				\tkzMarkAngle[size=1cm,color=cyan](X,Z,phi)
-				\tkzMarkAngle[size=1.5cm,color=cyan](theta,Z,Y)
-				\tkzLabelAngle[dist=1.6cm](theta,Z,Y){$\phi$}
-				\tkzLabelAngle[dist=1.1cm](X,Z,phi){$\theta$}
-			\end{tikzpicture}
-
-			\begin{spacing}{.2}
-			In order to transform this pixel coordinate into x-y coordinates relative to the drone, a few key assumptions made are that:
-
-				\begin{itemize}
-					\item The camera behaves as a pinhole model
-					\item Each pixel in the frame takes up an approximately equal fraction of the field of view
-				\end{itemize}
-
-			A big pitfall in this model is that no distortion from the camera lens is accounted for; these effects are still being investigated.
-
-			\pagebreak
-				\textbf{Transformation}:
-
-				Pixel given from YOLO: $PIX$
-
-				Pixel number of the center: $PIX\_CTR = \frac{PIX\_MAX}{2}$
-
-				Define $\psi$ as portion of angle from center image to pixel detected:
-
-				\begin{center}
-					$\psi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
-				\end{center}
-
-				To find the real coordinate ($REAL$) relative to the drone in the $X$ direction, There are two cases:
-
-						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$, Then:
-						\begin{center}
-							$REAL = z * tan(\theta + \frac{\psi}{2})$
-						\end{center}
-						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$, Then:
-						\begin{center}
-							$REAL = z * tan(\theta - \frac{\psi}{2})$
-						\end{center}
-				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
-
-						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$
-						\begin{center}
-							$REAL = z * tan(\theta - \frac{\psi}{2})$
-						\end{center}
-						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$
-						\begin{center}
-							$REAL = z * tan(\theta + \frac{\psi}{2})$
-						\end{center}
-				This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ `top' of frame is $PIX\_MAX$ and bottom is $1$.
-			\end{spacing}
-
-		Once the coordinate X, Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the `gym reference frame.' The gym reference frame is defined as a right-handed coordinate system starting in the bottom left-hand corner of the field where the green line meets the outer white line.
-This transformation is defined as follows:
-
-		\begin{center}
-			$yawAngle = currentHeading - GymOffset$
-		\end{center}
-		\begin{center}
-			$roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone$
-		\end{center}
-
-		\[
-		R(3) =
-			\begin{bmatrix}
-			cos(yawAngle) & -sin(yawAngle) & 0 \\
-			sin(yawAngle) & cos(yawAngle)  & 0 \\
-			0 & 0 & 1
-			\end{bmatrix}
-		\]
-
-		CR is the correction vector formulated from the corner detection vision algorithm.
-EKFdronePose is the position of the drone queried from the Pixhawk.
-R(3) is the rotation matrix about the third axis.
-GymOffset is the direction of the 2 axes defined during the startup sequence before flight.
-The new coordinate in the gym frame is passed off to the strategy node as data to be acted on.
-	\subsection*{Threat Avoidance}
-		Our avoidance system takes data from a 2D LiDAR that is used to identify the obstacle Roombas.
-This data is passed and the strategy node uses this data to weigh possible movements negatively based on their relative position to the obstacle Roombas.
-The controls node also will use the data, such as in the event an obstacle robot is within 1.5 [m], in which case controls node will issue a waypoint opposite of the minimum vector.
-
-	\subsection*{Communications}
-		On the Jetsons, data is passed between software nodes via ROS.
-Data in between our multiple Jetsons is passed via ROS messages through direct ethernet connections.
-Commands to the flight computer are passed via serial connection with data encoded in MAVLINK messages.
-
 	\subsection*{Power Management System}
@@
 
-		\begin{figure}[!htbp]
-			\begin{center}
-				\includegraphics[width=0.75\textwidth]{powerGraph}
-			\end{center}
-		\end{figure}
+%		\begin{figure}[!htbp]
+%			\begin{center}
+%				\includegraphics[width=0.75\textwidth]{powerGraph}
+%			\end{center}
+%		\end{figure}
 
@@
 
+	\subsection*{Flight Control System}
+		\subsubsection*{Navigation/State Estimation System}
+
+			Our system builds off of the robust open source project ArduCopter.
+ArduCopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude ToF, and the optical flow.
+The ArduCopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
+The vast community of developers and users ensures refined controls code with lots of features.
+
+			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin.
+This has been done to make our drones capable of navigating in GPS denied environments.
+For general waypoint navigation, the drones utilize the ArduCopter EKF that takes in data from the sensors listed above, including the optical flow, compass, and IMU.
+The EKF position is then queried via mavros so that our controls code can use our position to make intelligent decisions.
+Additionally, our drones use ORBSLAM running on the Jetson to provide localization data in flight to augment the data from the optical flow sensor while in areas where the ground does not have a textured surface.
+After those localization and navigation sensors, the controls node also takes in data from the sonar sensors.
+The controls node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint until the drone has reached its destination.
+Over time, the EKF will have some error in comparison to reality.
+However, using ORBSLAMM, an open-source version of ORBSLAM that contains multimapping, we are able to combat this by correcting the maps through visuals of physical objects (which will not be moving), which is then used to correct the EKF.
+
+		\subsubsection*{Attitude/Position Control System}
+
+			Another aspect of navigating in a GPS-denied is concrete information on our position.
+Using a Teraranger One Time of Flight sensor from Terabee, our drones are able to know their exact altitude.
+This sensor was chosen due to its extremely light weight over other LiDAR options.
+This communicates over I2C directly to the Pixhawk where ArduCopter uses that information in the EKF.
+
+			The position control aspect is handled through ORBSLAM running on the Jetson which is then fed into ArduCopter on the Pixhawk.
+The stereo camera in the front of the aircraft allows visual and depth information of the objects on the field and is used for our position.
+Additionally, ORBSLAM can potentially fail to get accurate tracking of objects if the drone translates too quickly.
+This is augmented through the optical flow sensor, which, while not as useful on the non-textured surface should at least ensure that the drone does not lose control.
+
+			The quadcopter uses eight sensors for flight control.
+The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.
+
+			The 1D LiDAR module used is a Time of Flight (ToF) sensor named the Teraranger One.
+This one-dimensional sensor is directed downward and provides data to determine altitude.
+The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction.
+The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses.
+The data from these sensors is used by the Pixhawk onboard system for flight control and maneuvering of the quadcopter.
+
+%		\begin{figure}[!htbp]
+%			\begin{center}
+%				\includegraphics[width=0.75\textwidth]{system}
+%				\caption*{Overview of control system}
+%			\end{center}
+%		\end{figure}
+
+		\subsubsection*{Flight Termination System}
+			We will be using ArduCopter's EmergencyStop to act as our killswitch.
+In the event of catastrophic failure, the safety operator can send the kill signal, and all power will immediately be cut from the drone's ESCs, and in turn, the motors.
+
+\section*{MISSION PACKAGE}
+	The drone has been designed to carry all the necessary GNC sensors, an array of sonar sensors, a stereo camera, a downward camera, and a Nvidia Jetson TX2.
+In addition, the drone carries a telemetry radio, WiFi antennas, and an RC receiver in order to carry out safe flight.
+	\subsection*{Perception System}
+		\subsubsection*{Target Identification and Behavior}
+			For target identification and behavior, the drones fly to defined waypoints where the quadrants of the QR codes are located.
+Computer vision begins to process the quadrant that is in view.
+Through our algorithm that uses the inherent features of QR codes, the drone is able to narrow down
+
+			For target identification, the drone carries four Logitech C270 USB webcams and one Logitech C210 USB webcam.
+One of the cameras is located at the bottom of the drone and faces straight downward.
+The other four cameras are mounted on the bottom side of each arm facing outward.
+All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.
+
+			There are two main objectives that need to be completed to successfully relay target information to the strategy node.
+The first objective is to take in the raw video data and detect the target Roombas so that pixel numbers of the centroids of the Roombas in the frame can be sent as output.
+The second objective is to take the pixel numbers of the centroids of the detected Roombas as input, and then output x and y coordinates relative to the drone using a coordinate transformation and the known height and orientation of the camera with respect to the floor.
+
+			In order to accomplish the first objective, an open source software package developed by Joseph Redmon called YOLO (You Only Look Once) is used.
+More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher framerates.
+YOLO is a neural network that can identify user-defined objects once it has been trained.
+After training the neural network by feeding in approximate 2000 photos of the target Roombas (with the Roombas identified manually), YOLO can reliably identify target Roombas in real time.
+
+		\subsubsection*{Threat Identification and Behavior}
+			Our avoidance system takes data from a 2D LiDAR that is used to identify the obstacle Roombas.
+This data is passed and the strategy node uses this data to weigh possible movements negatively based on their relative position to the obstacle Roombas.
+The controls node also will use the data, such as in the event an obstacle robot is within 1.5 [m], in which case controls node will issue a waypoint opposite of the minimum vector.
+
+			For completion of Mission 8, the drone must be able to detect the QR code and avoid obstacles, both moving and non-moving.
+The quadcopter is equipped with a single downward facing camera for reading the quadrant of the QR code.
+A stereo camera is used for ORBSLAMM for localization.
+There is also an array of sonar sensors for obstacle avoidance.
+
+			The singular bottom camera is a ELP webcam.
+This webcam is used for reading the QR code quadrant.
+The stereo camera in front is also an ELP camera.
+These cameras were chosen for their very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad.
+			The array of sonar sensors contains 4 MAXBOTICS 7m I2C sonars.
+These allow the drone to detect objects on the sides the quadcopter intends to move in.
+We chose to use this for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power.
+Sonar sensors are very tried and true.
+Additionally, we opted for sonar rather than radar as radar has a harder time picking up smaller objects, like a drone.
+
+		\subsubsection*{Gesture Identification and Behavior}
+			Android app, PocketSphinx.
+
+	\subsection*{Communications Systems}
+		On the Jetsons, data is passed between software nodes via ROS.
+Data in between our multiple Jetsons is passed via ROS messages through direct ethernet connections.
+Commands to the flight computer are passed via serial connection with data encoded in MAVLINK messages.
+
+		Networking between drones handled through WiFi 2.4 GHz.
+
+	\subsection*{Man/Machine Interface}
+		The drone has a DX7 RC controller interface for system checks and emergency situations.
+In addition, the flight controller can be monitored via a telemetry radio using Mission Planner.
+Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.
+
 \section*{OPERATIONS}
@@
 				\item Check battery voltage (12.0-12.6V) and insert
-				\item Make sure LiDAR and PX4FLOW are not covered
-				\item Make sure that ESCs are plugged in to the right pins
+				\item Make sure LiDAR, PX4FLOW, and cameras are not covered
+				\item Make sure that the props are on in the correct direction (leading edge in)
 				\item Make sure prop guards are secure
-				\item Make sure that the props are on in the correct direction (leading edge in)
-				\item Make sure that the props are not upside down
-				\item Make sure props are clear of any structures
-				\item Make sure Kill Switch is in off position
+				\item Make sure Kill Switch is in correct position
 				\item Power on controllers
-				\item Make sure TELEM2 is unplugged
-				\item Plug in power loop
-				\item Turn Kill Switch to on position
 				\item Make sure ground station has good telemetry
@@
 			\end{my_enumerate}
-	\subsection*{Man/Machine Interface}
-		The drone has a DX7 RC controller interface for system checks and emergency situations.
-In addition, the flight controller can be monitored via a telemetry radio using Mission Planner.
-Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.
 
 \section*{RISK REDUCTION}
-	\subsection*{Vehicle Status}
+	\subsection*{Vehicle Design}
+		\subsubsection*{EMI/RFI Solutions}
+		The Arducopter flight stack helps keep interference risk down through the EMI calibration on the Pixhawk.
+The calibration calculates the magnetic interference correction by formulating a function of the magnetic interference based on the power setting of the motors.
+
 		\subsubsection*{Shock/Vibration Isolation}
@@
 Because of this, nominal landings will not interfere with the guidance or navigation of the drone.
-
-		\subsubsection*{EMI/RFI Solutions}
-		The Arducopter flight stack helps keep interference risk down through the EMI calibration on the Pixhawk.
-The calibration calculates the magnetic interference correction by formulating a function of the magnetic interference based on the power setting of the motors.
 
@@
 
-	\subsection*{Testing}
+	\subsection*{Physical Testing}
 		Simulation, however, can only prove so much.

### 2019-06-01 IARC_Paper_2019/Paper.tex
Getting closer to done

@@
 \section*{INTRODUCTION}
-	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone.
-Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone.
-Thus, Mission 8 requires novel solutions to deriving this critical telemetry as GPS is forbidden.
+	Previous aerial robotics missions have always allowed for GPS or other external active position estimation that allowed for constant locational awareness.
+Location data is important to any mission, as proper state awareness prevents various failures, including complete loss of control for the drone.
+Thus, Mission 8 requires novel solutions to deriving this critical state data as GPS is forbidden.
 Additionally, the aircrafts must be capable of taking commands in a humanized "natural" fashion and avoid other aircrafts without being informed of those other aircrafts' locations.
@@
 	Texas Aerial Robotics addresses these challenges by utilizing computer vision.
-TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena while in flight and use that data in real time.
-The drone creates pointclouds of the objects in view using the stereo camera and combines sections together.
+TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena in real time.
+The drone creates pointclouds of the objects in view using the stereo camera and combines sections together to create the maps.
 This means that should a section of the map start showing drift, the ORBSLAM2/ORBSLAMM System will toss out just the section while maintaining as much of the map as possible.
@@
 	\pagebreak
-	\subsection*{Yearly Milestones}
+	\subsection*{Texas Aerial Robotics Yearly Milestones}
 
-	2019 - Have a working system, with localization and GPS-denied navigation of multiple drones.
+	\begin{itemize}
+
+		\item 2017 (Mission 7) - Have a working bot, with computer vision software in nearly working state
+
+		\item 2018 (Mission 7) - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, and tweak the physique of the drone for better flight control and stability
+
+		\item 2019 (Mission 8) - Complete a working system, with localization and GPS-denied navigation of multiple drones.
 These drones should work together to solve the QR code and communicate with a person through an Android app that can transmit voice commands to the drones.
 
-	2020 - Finish all aspects of mission through more networking between the quadcopters, tweak the physique of the drone for better flight control and stability, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible.
+		\item 2020 (Mission 8) - Finish all aspects of mission through more networking and collaboration between the quadcopters, improve the drone for better flight control and overall size, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible.
+	\end{itemize}
 
@@
 			Our system builds off of the robust open source project ArduCopter.
-ArduCopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude ToF, and the optical flow.
+ArduCopter, which runs on the Pixhawk, controls the stability and position control of the drone by taking in data from the IMU, compass, altitude ToF, and a position estimate generated from our optical flow sensor or ORB SLAM.
 The ArduCopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones.
-The vast community of developers and users ensures refined controls code with lots of features.
+The vast community of developers and users ensures reliable controls code with lots of features.
 
-			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin.
+			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin from our GNC ROS node.
 This has been done to make our drones capable of navigating in GPS denied environments.
 For general waypoint navigation, the drones utilize the ArduCopter EKF that takes in data from the sensors listed above, including the optical flow, compass, and IMU.
-The EKF position is then queried via mavros so that our controls code can use our position to make intelligent decisions.
-Additionally, our drones use ORBSLAM running on the Jetson to provide localization data in flight to augment the data from the optical flow sensor while in areas where the ground does not have a textured surface.
-After those localization and navigation sensors, the controls node also takes in data from the sonar sensors.
-The controls node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint until the drone has reached its destination.
-Over time, the EKF will have some error in comparison to reality.
-However, using ORBSLAMM, an open-source version of ORBSLAM that contains multimapping, we are able to combat this by correcting the maps through visuals of physical objects (which will not be moving), which is then used to correct the EKF.
+The EKF position is then queried via mavros so that our navigation code can use our position to make intelligent decisions.
+TAR has greatly improved ArduCopter’s GPS denied capabilities by integrating ORBSLAM into the ArduCopter EKF.
+The use of ORBSLAM allows the drone to navigate based on 3 dimensional visual features in the drones operating environment.
+ORBSLAM continuously builds a map of its environment and compares current local maps to its master.
+Because of this comparison algorithm, ORBSLAM is able to perform loop closure which is useful in negating any propagated error from the rate sensors.
+
+			In addition to the stability and position control from ArduCopter, TAR’s drone sports a navigation node, which executes our pathplaning algorithms developed for Mission 8.
+The navigation node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint to ArduCopter until the drone has reached its destination.
 
@@
 
-			Another aspect of navigating in a GPS-denied is concrete information on our position.
+			A crucial aspect of navigating in a GPS-denied is concrete information on our position.
 Using a Teraranger One Time of Flight sensor from Terabee, our drones are able to know their exact altitude.
@@
 			The position control aspect is handled through ORBSLAM running on the Jetson which is then fed into ArduCopter on the Pixhawk.
-The stereo camera in the front of the aircraft allows visual and depth information of the objects on the field and is used for our position.
-Additionally, ORBSLAM can potentially fail to get accurate tracking of objects if the drone translates too quickly.
-This is augmented through the optical flow sensor, which, while not as useful on the non-textured surface should at least ensure that the drone does not lose control.
+The stereo camera in the front of the aircraft allows visual and depth information of the objects on the field.
+This information is used to formulate an estimate of the drone’s position based on the 3 dimensional visual features of the environment.
+In addition, these features are compared to features the drone has already seen in order to perform loop closure.
+Loop closure is then used to correct for propagated error accumulated from the drone’s rate sensors.
+No sensor or algorithm is foolproof.
+ORBSLAM has some limitations which limit the algorithms ability to generate position estimates.
+First, if the camera is moved too quickly, the deltas between frames is too large and ORBSLAM can lose tracking.
+This is mostly mitigated by limiting the drones flight velocity.
+The second limitation of ORBSLAM is the requirement of textures and 3D features.
+Both of these risks are low when operating in the Mission 8 arena, however, this is a flight critical system and the consequence of failure are catastrophic.
+TAR has opted to implement redundancy by attaching the PX4FLOW sensor to supplement ORBSLAM in the event of failure.
+While not as useful on the non-textured surface, it should at least ensure that the drone does not lose control.
 
@@
 The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction.
+As previously stated this sensor is a redundancy for ORBSLAM.
 The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses.
@@
 	\subsection*{Perception System}
-		\subsubsection*{Target Identification and Behavior}
-			For target identification and behavior, the drones fly to defined waypoints where the quadrants of the QR codes are located.
-Computer vision begins to process the quadrant that is in view.
-Through our algorithm that uses the inherent features of QR codes, the drone is able to narrow down
-
-			For target identification, the drone carries four Logitech C270 USB webcams and one Logitech C210 USB webcam.
-One of the cameras is located at the bottom of the drone and faces straight downward.
-The other four cameras are mounted on the bottom side of each arm facing outward.
-All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.
-
-			There are two main objectives that need to be completed to successfully relay target information to the strategy node.
-The first objective is to take in the raw video data and detect the target Roombas so that pixel numbers of the centroids of the Roombas in the frame can be sent as output.
-The second objective is to take the pixel numbers of the centroids of the detected Roombas as input, and then output x and y coordinates relative to the drone using a coordinate transformation and the known height and orientation of the camera with respect to the floor.
-
-			In order to accomplish the first objective, an open source software package developed by Joseph Redmon called YOLO (You Only Look Once) is used.
-More specifically, the TinyYolo version of YOLO was elected to be used since it is lighter and can obtain higher framerates.
-YOLO is a neural network that can identify user-defined objects once it has been trained.
-After training the neural network by feeding in approximate 2000 photos of the target Roombas (with the Roombas identified manually), YOLO can reliably identify target Roombas in real time.
-
-		\subsubsection*{Threat Identification and Behavior}
-			Our avoidance system takes data from a 2D LiDAR that is used to identify the obstacle Roombas.
-This data is passed and the strategy node uses this data to weigh possible movements negatively based on their relative position to the obstacle Roombas.
-The controls node also will use the data, such as in the event an obstacle robot is within 1.5 [m], in which case controls node will issue a waypoint opposite of the minimum vector.
-
 	For completion of Mission 8, the drone must be able to detect the QR code and avoid obstacles, both moving and non-moving.
@@
 
-			The singular bottom camera is a ELP webcam.
-This webcam is used for reading the QR code quadrant.
-The stereo camera in front is also an ELP camera.
-These cameras were chosen for their very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad.
-			The array of sonar sensors contains 4 MAXBOTICS 7m I2C sonars.
-These allow the drone to detect objects on the sides the quadcopter intends to move in.
-We chose to use this for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power.
+		\subsubsection*{Target Identification and Behavior}
+			For target identification and behavior, the drones fly to defined waypoints where the quadrants of the QR codes are located.
+Each quadcopter is equipped with a singular ELP webcam facing downward.
+This camera was chosen for its very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad.
+
+			Once the QR code quadrant is in view, computer vision begins to process using our algorithm that uses the inherent features of QR codes.
+Any drone is able to narrow down the 4 digit combination to approximately 6 permutations that from only the bottom-right quadrant.
+The drones continue to scan the other sections of the QR code and piece together the combination.
+If the top-right quadrant is found, then the code is complete with only the top-right and bottom-right sections.
+
+			After the code has been identified, the quadcopters fly to positions on the field where the human would likely choose to heal and await other commands.
+
+		\subsubsection*{Threat Identification and Behavior}
+			Our avoidance system takes data from an array of sonar sensors.
+These 4 MAXBOTICS 7m I2C sonars allow the drone to detect objects on the sides the quadcopter intends to move in.
+This data is passed to the navigation node, which uses this data to determine if an obstacle drone or a wall is within 1.5 [m], in which case the node will issue a waypoint opposite the detections.
+Edge cases and corner cases have also been accounted for, such as the case where an enemy drone pushes a helper drone against a wall.
+In this case, the drone will either rise or fall in altitude, depending on the distance from the ground.
+Each drone has its own array of sonar sensors, so even in the event of communication failures between quadcopters in the full system, each drone will continue to intelligently avoid dangerous situations.
+
+			Sonar sensors were chosen for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power.
 Sonar sensors are very tried and true.
-Additionally, we opted for sonar rather than radar as radar has a harder time picking up smaller objects, like a drone.
+As we use I2C as our communication protocol for these sonars, adding or subtracting sensors to the array becomes trivial, with easy addition of more sonar sensors (up to a limit of 127) with very few modifications to the code, electrical systems, and/or hardware, aside from the physical mounting of the new sonars themselves.
+Additionally, sonar was picked over radar as radar has a harder time picking up smaller objects, like a drone.
+
+			Other threat identification systems, such as an infrared cameras, were discussed.
+However, potential interference from sunlight and other environmental factors led the team to choosing sonars instead.
 
@@
 	\subsection*{Communications Systems}
-		On the Jetsons, data is passed between software nodes via ROS.
-Data in between our multiple Jetsons is passed via ROS messages through direct ethernet connections.
-Commands to the flight computer are passed via serial connection with data encoded in MAVLINK messages.
-
-		Networking between drones handled through WiFi 2.4 GHz.
+		On each Jetson, data is passed between software nodes via ROS.
+Commands to the flight computer from that Jetson are passed via serial connection with data encoded in MAVLINK messages.
+Data between our multiple Jetsons (1 per drone) is passed via ROS messages through a 2.4 GHz WiFi network.
+The quadcopters connect to Texas Aerial Robotics’ router, which maps the quadcopters to IP addresses.
+The drones are interchangeable on the network-side too as the drones to IP addresses is not hard defined, resulting in a more modular and more robust system.
 
@@
 		\subsubsection*{EMI/RFI Solutions}
-		The Arducopter flight stack helps keep interference risk down through the EMI calibration on the Pixhawk.
+		The Arducopter flight stack helps keep interference risk down through the EMI motor calibration on the Pixhawk.
 The calibration calculates the magnetic interference correction by formulating a function of the magnetic interference based on the power setting of the motors.
+Additionally, the drone was designed to reduce the electromagnetic interference in the first place through the use of carbon fiber over the high voltage electronics.
+Antennas and other radio connections are then done above the carbon fiber.
 
@@
 The team decided that there is no need for extra damping.
-After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts.
-The team believes there is no need to have landing shocks, as the sophisticated Arducopter flight stack has logic to recognize landing.
+After completion of our drones, flight logs from the Pixhawk confirmed that vibration on the quadcopter was well within recommended amounts.
+The team believes there is no need to have landing shocks, as the sophisticated ArduCopter flight stack has logic to recognize landing.
 Because of this, nominal landings will not interfere with the guidance or navigation of the drone.
@@
 Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
-	\nocite{redmon2016yolo9000}
-	\nocite{GitHubSPACEROBOTICS}
-	\nocite{HoughTransform}
-	\nocite{CannyEdgeDetection}
+	\nocite{ORBSLAM2}
+	\nocite{daoud2018slamm}
 	\bibliography{bibliography}

### 2019-06-01 IARC_Paper_2019/Paper.tex
Close to done

@@
 
+	One important aspect of TAR’s system is that it is very modular and interchangeable.
+Drone A is meant to be identical to Drone B and each drone can operate as any other.
+This creates a more robust drone swarm as the mission is still doable with as few or as many drones and no one drone is the hinge that the entire system needs to function.
+
 	\begin{figure}[!htbp]
@@
 
-		\item 2017 (Mission 7) - Have a working bot, with computer vision software in nearly working state
+		\item 2017 (Mission 7) - Have a working bot, with computer vision software in nearly working state for IARC Mission 7, a Roomba herding challenge.
 
-		\item 2018 (Mission 7) - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, and tweak the physique of the drone for better flight control and stability
+		\item 2018 (Mission 7) - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, and tweak the physique of the drone for better flight control and stability.
 
@@
 
-%		\begin{figure}[!htbp]
-%			\begin{center}
-%				\includegraphics[width=0.75\textwidth]{system}
-%				\caption*{Overview of control system}
-%			\end{center}
-%		\end{figure}
+		\begin{figure}[!htbp]
+			\begin{center}
+				\includegraphics[width=0.75\textwidth]{system}
+				\caption*{Overview of control system}
+			\end{center}
+		\end{figure}
 
@@
 		\subsubsection*{Gesture Identification and Behavior}
-			Android app, PocketSphinx.
+		For the humanized controls, TAR opted not to go for gesture recognition as gesture recognition poses many challenges regarding identifying which drone is being commanded and the characteristics of the person, such as height and size.
+Additionally, the person needs to get the QR code information from the drones.
+For this TAR developed an Android app.
+Once we had the Android app, it became clear that voice recognition made more sense for commanding the air vehicles.
+The voice recognition is done on the Android device and the information is sent over the 2.4 GHz WiFi network to the drone that is being commanded.
+The details of this app is defined in the Man/Machine Interface subsection below.
 
@@
 
+		A crucial part of the Man/Machine Interface is the Android app that handles humanized communication to and from the air vehicles.
+Texas Aerial Robotics was able to spin this up quickly by using the same method of building off open-source projects.
+For this Android application, we built off ROSJava (running on the Android phone) to be able to open ROS Subscribers and Publishers on a remote device (the drones).
+The drones can publish to the Android phone once they have completed the QR code and the Android phone displays the data.
+Additionally, this Android app also handles the voice recognition aspect.
+Using the open-source project PocketSphinx from Carnegie Mellon University, TAR was able to implement on device voice recognition with a custom command dictionary.
+This was developed in a seperate app until ready.
+Then the two apps were combined to give one view for communicating to and from the drones over ROS from that Android device.
+TAR will use headphones with a clip-on microphone for listening to the person so the voice is clear.
+This app was developed with the ability to use it on Android Wear as well, so a user could just as easily use a smartwatch as the interface device for commanding the drones.
+
 \section*{OPERATIONS}
@@
 			\begin{my_enumerate}
-				\item Check battery voltage (12.0-12.6V) and insert
+				\item Check battery voltage and insert
 				\item Make sure LiDAR, PX4FLOW, and cameras are not covered
@@
 After completion of our drones, flight logs from the Pixhawk confirmed that vibration on the quadcopter was well within recommended amounts.
-The team believes there is no need to have landing shocks, as the sophisticated ArduCopter flight stack has logic to recognize landing.
-Because of this, nominal landings will not interfere with the guidance or navigation of the drone.
+The team believes there is no need to have landing legs or landing shocks.
+In flight, the drone stays stable and the sensors give good readings throughout the 20 minutes of flight time each drone can get.
+Because of this, TAR believes no inflight shocks or vibrations will interfere with the guidance or navigation of the drone.
 
@@
 		We took significant steps to ensure safe operation of the quadcopter.
-In order to keep the quadcopter from flying where we do not want, we have a Spektrum receiver module onboard so our designated pilot can manually control the vehicle.
+In order to keep the quadcopter from flying where we do not want, we have a Spektrum receiver module onboard so our designated safety pilot can manually control the vehicle.
 Additionally, we are able to check the status of the quadcopter through our telemetry to our ground station.
-The structure of the drone is also outfitted with prop guards to mitigate damage to people or property in the event of catastrophic failure.
-Our prop guards took multiple iterations.
-We wanted a design that would not interfere with the prop wash, but still be able to prevent damage to the quadcopter itself in the unfortunate event of a collision.
-The first iteration looked nice, but interfered with the prop wash too much and weighed too much, reducing the thrust.
-However, the next iteration cut weight and did not interfere with the prop wash.
+
+An important part of IARC Mission 8 is the Human in the Loop.
+Safety is dialed up to 11 when a person is near the quadcopters.
+For this, each drone is outfitted with propeller guards to mitigate damage to people or property.
+We wanted a design that would interfere with the prop wash as little as possible, but still be able to prevent a human from accidentally sticking a finger in the path of the blades.
+These prop guards protect the drone from damage, but more importantly, the human from damage.
+These prop guards are also easily removable, should a situation arise where the quadcopter not need the guards or parts need to be quickly replaced.
+
+Also an important safety feature is the sonar sensor array discussed earlier. This important feature keeps each drone from getting close to anything in flight in the first place.
+
+The last important safety feature is the kill switch.
+The kill switch is one developed by the ArduCopter team.
+Should the kill command be sent, the Pixhawk shuts off the ESCs immediately.
+This has been a feature of ArduCopter for multiple software versions and has been tested all around the world.
+Because of its testing through being in ArduCopter, it is a far more tried and true method than one TAR could implement otherwise.
 
 	\subsection*{Modeling and Simulation}
+	For Mission 8, the computational team developed a simulation of Mission 8 with Gazebo and ROS software.
+With this simulation, TAR was able to perform software in the loop simulation and conduct mission planning without jeopardizing the physical drone.
 
-		To safely test our software throughout the development process, the team implemented a simulation using the Gazebo application.
-Using this tool, TAR was able to deploy full-scale software in the loop simulation without jeopardizing hardware with each design iteration.
+	The simulation was first constructed by building models according to the specifications provided by IARC.
+The models were built in Solidworks and edited with Blender software to texture the models and export as COLLADA files.
+With these COLLADA files, the properly textured models were loaded into the Gazebo simulation.
+The models constructed consisted of the arena, the bunkers, the bins, and the QR codes.
+Moreover, a controllable human was inserted into the simulation.
+To simulate the helper drone(s), TAR imported a standard quadcopter model from the ArduCopter standard library, similar to what was done for Mission 7.
+On the drone model, TAR added the same sensors used on the physical drone such as stereo cameras and sonar.
+With this model, all the software components of the drone such as the flight code and ORBSLAM2 could be tested.
 
-		To employ the Gazebo framework, the team imported a standard quadcopter model from the ArduCopter standard library and Roomba models from Gazebo model library, which were then updated with the color-coded plates and obstacle tubes prescribed for the competition.
-Additionally, the ground plane within the reproduction was changed to match the texture expected at the competition.
+	Going into more detail, the human model was made controllable with C++ scripts that utilized ROS software to input movement commands.
+Likewise, the drone was controlled through ArduCopter and ROS and demonstrated the desired autonomous behavior that was to be congruent with the actual physical drone’s behavior.
+Also, for added robustness, the QR codes within the arena could be randomly changed through a simple bash script; this allowed us to quickly test our QR code reading with different QR code combinations.
 
-		Gazebo was chosen because of its compatibility with ROS and Ardupilot, the internal communication protocol employed onboard our drone.
-With this congruence, the exact same software run onboard the drone could be run within the simulation, complete with sensor feedback detected within the simulated instance.
-C++ scripts could then be utilized to enforce the correct Roomba behaviors, scripting the robots using the same messaging environment as the quadcopter itself (ROS).
+	Lastly, with hardware generously donated to us by Emergent Space Technologies, Virtual Reality (VR) was implemented into the human model for mission planning and demonstration.
+We added a camera to the human model’s head and exported the feed to the VR headset to simulate what it would actually be like to be inside the arena.
+With this perspective, the team had a unique insight into the conditions of the arena that would be otherwise unobtainable without physical access to the actual arena.
 
-		Overall, modeling our software behavior within a Gazebo simulation greatly expedited the development process.
-By standardizing the simulation setup, tests could be conducted on multiple computers at any time, instead of requiring the sluggish process of updating, calibrating, and flying the physical drone.
-Additionally, simulation protected the hardware from the accidents and unintentional flight behavior inherent to prototype software.
+	With this simulation, Texas Aerial Robotics is able to test drone software and perform mission planning without posing any risk to the physical drone, saving it from any potential accidents and unintentional flight behavior inherent to prototype software.
+Additionally, by standardizing the simulation setup, tests could be conducted on multiple computers at any time, allowing for more teammates to do their respective testing on the drone concurrently.
 
@@
 Eventually, refined software was tested on a model testbed or on the drone itself.
-Much of the computer vision and general software integration was developed on this testbed, where performance could be verified with the same sensors and computational hardware as the aircraft before full-scale deployment.
+Much of the obstacle avoidance and general software integration was developed on this testbed, where performance could be verified with the same sensors and computational hardware as the aircraft before full-scale deployment.
 Even strategy nodes could be tested on this platform, with waypoint predictions vetted before being deployed to the aircraft.
@@
 
-		However, summer development saw additional test flights conducted in a vacant parking garage, but both locations suffered from magnetic inconsistencies which interfered with compass calibrations.
-Because of this, later tests, including the qualifying run submitted, were conducted in a parking lot to the north of the university.
+Texas Aerial Robotics did learn last year that testing outdoors is no substitute for testing in a gym.
+However, obtaining a gym that will allow TAR to fly has been extremely difficult.
+TAR is still working on being able to test inside gyms to more closely replicate the compass and other sensor interference that comes from being inside a closed metal structure.
+Ideally, TAR will run full scale tests in gyms prior to competition, but realistically much of our testing will be done outdoors again this year.
 
-		Regardless of the setting, each flight test was conducted with constant apparatus: a four meter by four meter test mat printed with the pattern expected at competition to allow optical flow for navigation.
-Across this mat drives a test Roomba, which accurately recreates both the physical appearance and behaviors of those robots that will be tracked at the venue, complete with top plate and switch.
-Finally, there is the drone itself, which starts on a corner of the mat, takes off autonomously, and then executes the maneuver to be tested.
+In the year following, however, the University is setting up a robotics facility which will allow TAR to test indoors.
+Until then, TAR takes testing very seriously, but mostly in simulation and then outdoors.
 
 \section*{CONCLUSION}
-	Texas Aerial Robotics' solutions to the challenges provided by IARC Mission 7 are bountiful and diverse.
-The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success.
-Unique software utilizes input from an expansive collection of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area.
-Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
+	From the framework conceived from Mission 7 and Texas Aerial Robotics’ hard work from Fall 2018 to the present, significant strides have been made in the hardware, computer vision, controls, and computational areas to provide robust solutions for the challenges presented by Mission 8.
+Through all of Texas Aerial Robotics’ progress, the autonomous drones built for this competition have been optimally designed to house all the instruments necessary for mission success while maintaining the stability, safety, and endurance requirements of Mission 8.
+Moving forward, the drone will undergo more physical and simulation testing, and the software and hardware will be continuously improved upon to ensure that the probability of success for Mission 8 is as high as possible.
 	\nocite{ORBSLAM2}

### 2019-06-01 IARC_Paper_2019/Paper.tex
Getting close to done. Added some hardware stuff.

@@
 The frame is lifted by four T-Motor MN2212 KV920-V2.0 motors.
-These motors provide
-			------------fix these numbers---------- 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 7.2 [kg] of thrust.
-This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.
+These motors provide 0.92 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 3.68 [kg] of thrust.
+This is necessary for our 1.95 [kg] weight to maintain a thrust-to-weight ratio of 1.88, for battery life and flight time.
 
@@
 The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.
+
 	\subsection*{Power Management System}
-The quadcopter uses a 10000 [mAh] 4S 10C LiPo battery and a 2000 [mAh] 3S 15C LiPo battery for power.
-The 10000 [mAh] 4S 10C LiPo is used to power our ESCs and Motors.
-With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 [grams] of thrust per motor needed for hovering flight.
-The 2000 [mAh] 3S 15C LiPo will power the flight control board and Jetson compute units.
+The quadcopter uses a 4000 [mAh] 4S 25C LiPo battery for power.
+With 4 T-Motor MN2212 KV920-V2.0  motors running at close to 60\% throttle, a 4 Cell battery was necessary to reach the 480 [grams] of thrust per motor needed for hovering flight.
 \begin{center}
@@
 
-Assuming an average throttle of 65\% for maneuvering, we see a 9 A current draw from each motor, and with a 10 Ah battery, that provides us with 16 minutes of flight time with minimal maneuvering and height change.
+Assuming an average throttle of 65\% for maneuvering, we see a 4 A current draw from each motor, and with a 4000 mAh battery, that provides us with 13 minutes of flight time with minimal maneuvering and height change.
 This gives us plenty of headroom for more intense altitude and positioning changes, which will allow us to move more quickly during the competition, a valuable asset with the given time limitation.
@@
 
-To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 [A] and maximum practical current draw of 19.4 [A] required by the motors.
-The 10000 [mAh] battery with a 10C discharge rate gives us a maximum continuous current draw of 100 [A], matching the limit of the motors.
+To save on weight and space, we chose a 25C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 100 [A] and maximum practical current draw of 29.6 [A] required by the motors.
+The Pixhawk flight controller and Jetson TX2 compute unit will be powered of the same 4000 [mAh] battery.
+Together, they contribute a maximum practical current draw of 2.2 [A].
+The 4000 [mAh] battery with a 25C discharge rate gives us a maximum continuous current draw of 100 [A], well exceeding the limit of the motors and computing units combined.
 
-The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph].
+The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 8 minute flight times at speeds below 15 [mph].
 

### 2019-06-01 IARC_Paper_2019/Paper.tex
Small changes

@@
 
-\title{Intelligent Quadcopter for IARC 2019}
+\title{Humanized Quadcopter Swarm System for IARC 2019}
 
@@
 Thus, Mission 8 requires novel solutions to deriving this critical state data as GPS is forbidden.
-Additionally, the aircrafts must be capable of taking commands in a humanized "natural" fashion and avoid other aircrafts without being informed of those other aircrafts' locations.
+Additionally, the aircrafts must be capable of taking commands in a humanized ``natural'' fashion and avoid other aircrafts without being informed of those other aircrafts' locations.
 
 	Texas Aerial Robotics addresses these challenges by utilizing computer vision.
-TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena in real time.
+TAR uses ORBSLAM2, an ``Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras'' to create maps of the arena in real time.
 The drone creates pointclouds of the objects in view using the stereo camera and combines sections together to create the maps.
@@
 These drones also solve for the QR code that is the combination the human needs for collecting the objects.
-TAR implements the "humanized" control aspect of the system through voice control using an Android app that connects to all of the air vehicles.
+TAR implements the ``humanized'' control aspect of the system through voice control using an Android app that connects to all of the air vehicles.
 The drones are also built with safety features for a plethora of other objects that may be on the field through its man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.
@@
 
-The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 8 minute flight times at speeds below 15 [mph].
+The eCalc online tool was used to validate our calculations, and as seen by the generated graph, there should be no issue reaching 8+ minute flight times at speeds below 15 [mph].
 
-%		\begin{figure}[!htbp]
-%			\begin{center}
-%				\includegraphics[width=0.75\textwidth]{powerGraph}
-%			\end{center}
-%		\end{figure}
+		\begin{figure}[!htbp]
+			\begin{center}
+				\includegraphics[width=0.6\textwidth]{powerGraph}
+			\end{center}
+		\end{figure}
+
+\pagebreak
 

### 2019-06-01 IARC_Paper_2019/Paper.tex
I think done?

@@
 
-The eCalc online tool was used to validate our calculations, and as seen by the generated graph, there should be no issue reaching 8+ minute flight times at speeds below 15 [mph].
+The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times over 8 minutes at speeds below 15 [mph].
 
@@
 			\begin{center}
-				\includegraphics[width=0.6\textwidth]{powerGraph}
+				\includegraphics[width=\textwidth]{powerGraph}
 			\end{center}
@@
 \pagebreak
-
-As for the 2000 [mAh] 3S battery, this battery powers our Pixhawk flight controller and our three Jetson TX2 compute units.
-This was done partly to dedicate the entirety of the main battery to propulsion to maximize flight time.
-The other reason is that the speed controllers we chose (T-Motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution.
-2000 [mAh] was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.
 

### 2019-06-01 IARC_Paper_2019/Paper.tex
Submitted.

@@
 
-The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times over 8 minutes at speeds below 15 [mph].
+The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times of 8 minutes at speeds below 15 [mph].
 
@@
 ORBSLAM continuously builds a map of its environment and compares current local maps to its master.
-Because of this comparison algorithm, ORBSLAM is able to perform loop closure which is useful in negating any propagated error from the rate sensors.
+Because of this comparison algorithm, ORBSLAM is able to perform loop closure, which is useful in negating any propagated error from the rate sensors.
 
@@
 
-			A crucial aspect of navigating in a GPS-denied is concrete information on our position.
+			A crucial aspect of navigating in a GPS-denied area is concrete information on our position.
 Using a Teraranger One Time of Flight sensor from Terabee, our drones are able to know their exact altitude.
